---
title: "Untitled"
format:
  html:
    theme: default
---

# Getting Started

#### Libraries

```{r}
library(tidyverse)
library(lubridate) #To work with dates 
library(here)
library(base) #For ColSum
```

#### Data

```{r}
nrl<- read_csv(here("data","raw_data","nrl_dust_2022.csv")) #Dust concentration data set


```

Make Year-Month-Day_Hour column from yyymmddtt column

```{r}
nrl1<- nrl %>% 
  mutate(
    ymdh = ymd_h(nrl$yyyymmddhh))
```

Now switch it to CST **This dust dataset is in Coordinated Universal Time (UTC) and needs to be converted to Central Standard/Daylight Time (which is UTC-6 hours and UTC-5 hours for daylight savings.**

```{r}
nrl2<- nrl1 %>%
  mutate(
    cst = as_datetime(nrl1$ymdh, tz= c("America/Chicago"))) #CST/CDT
```

Make column with just date in CST

```{r}
nrl3<- nrl2 %>%
  mutate(
    just_date= as.Date(substr(nrl2$cst, 1,10)))

#Create hr for cst
#Make final DF with dust, hours, and time in CST
dust_final<- nrl3 %>%
  mutate(hr_cst = substr(nrl3$cst, 12,13)) %>%
  select(hr_cst, just_date, Dust) %>%
  rename(date=just_date)
  
```

**Now `dust_ind` data set has the date and hour of collection in CST/CDT, and the concentrations (AOD) at each time point**\

# Save RDS

```{r}
#Just dust data
saveRDS(dust_final, file = here("data", "processed_data", "dust", "dust_final.rds")) #Dust 
```
