---
title: "Vp qPCR"
format:
  html:
    theme: default
---

*This dataset is Daily Vp qPCR*

# Daily

Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
select<-dplyr::select
here<- here::here
mutate<-dplyr::mutate
```

Load data

```{r}
sq <-read_csv(here("data", "raw_data", 'qpcr', 'vp',  "vp_daily.csv")) 
```

Filter for HEX dye (samples). Cy5 is for IAC

```{r}
sq2<- sq %>% 
  select(SQ,Cq, Sample, Fluor) %>%
  filter(Fluor %in% "HEX")

```

Create Site Column from Sample Name

```{r}
site<- sq2 %>%
  mutate(site = substr(sq2$Sample,1,2)) #Creates new column `Site` from the first two letters in `Sample` (BO16 becomes BO)
```

Add Dilution Column and Filter column

```{r}
dilution<- site%>%
  mutate(dilution = case_when(site == "BO"~"10",#BO was 1:10
                              site  == "C2"~ "1",
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution)) 


filter<- dilution %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100",
                          Sample == "BO_7"~"100",
                          Sample == "BO_8"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_11"~"100",
                          Sample == "BO_12"~"50",
                          Sample == "BO_13"~"50",
                          Sample == "BO_14"~"50",
                          Sample == "BO_15"~"50",
                          Sample == "BO_16"~"30",
                          Sample == "BO_17"~"30",
                          Sample == "BO_18"~"30",
                          Sample == "BO_19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt)) 

```

Cq --> Copies/mL

```{r}
vp_LOD<- 3 #LOD copies per uL
```

```{r}
copies<- filter %>%
   mutate(
    copies_uL = SQ , 
    copies_uL= case_when((copies_uL == "NaN" | copies_uL < vp_LOD) ~ 0.5*vp_LOD, #50% LOD
                     TRUE ~ copies_uL),
    concentration_factor = 100/filter_amt, 
    copies_mL = copies_uL*concentration_factor*dilution, copies_uL)
```

```{r}
write_csv(copies, here('data', 'processed_data', 'ANOVA Data', 'vp_anova.csv'))
```

```{r}
copies<-
  copies %>%

select(Sample,copies_mL,site, copies_uL) 

```

Date Column

```{r}
date<- copies %>%
  dplyr::mutate(day = substr(copies$Sample,4,5)) %>% #Creates new column `day` 
  dplyr::mutate(date = case_when(day == "7"~"2022-07-07",
                         day ==  "8"~"2022-07-08",
                         day ==  "9"~"2022-07-09",
                         day ==  "11"~"2022-07-11",
                         day == "12"~"2022-07-12",
                         day ==  "13"~"2022-07-13",
                         day ==  "14"~"2022-07-14",
                         day ==  "15"~"2022-07-15",
                         day ==  "16"~"2022-07-16",
                         day == "17"~"2022-07-17",
                         day ==  "18"~"2022-07-18",
                         day == "19"~"2022-07-19"))

```

Take the average of qPCR triplicates

```{r}
final_d<- date %>% 
  group_by(site, Sample,date) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() %>% #Ungroup to spit everything back out 
  select(date,copies_mL,site)
```

Save as RDS and manually add date in excel

```{r}
#stop() #Write error so it wont overwrite
write.csv(final_d, file= here("data","processed_data","vp_clean_copies.csv"))
```

------------------------------------------------------------------------

# Monthly

*This dataset is Monthly Vp qPCR*

Load data

```{r}
sq <-read_csv(here("data", "raw_data", 'qpcr', 'vp', "vp_mon.csv")) 
```

Filter for HEX dye (samples). Cy5 is for IAC

```{r}
sq2<- sq %>% 
  select(SQ,Cq, site, Fluor, day) %>%
  filter(Fluor %in% "HEX")

```

Add Dilution Column and Filter column

```{r}
dilution<- sq2%>%
  mutate(dilution = case_when(site == "BO"~"1", #BO was 1:1
                              site  == "C2"~ "1",
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution)) 


filter<- dilution %>%
   mutate(filter_amt = case_when(
                          site == "BO" & day == 2 ~"100",
                          site == "BO" & day == 3 ~ "100",
                          site == "BO" & day == 4 ~ "100",
                          site == "BO" & day == 511 ~"100",
                          site == "BO" & day == 520 ~ "100",
                          site == "BO" & day == 524 ~ "100",
                          site == "BO" & day == 6 ~"100",
                          site == "BO" & day == 8~ "30",
                          site == "BO" & day == 9~"45",
                          site == "BO" & day == 10 ~ "60",
                          site == "BO" & day == 11~ "30",
                          site == "BO" & day == 12~ "60",
                          site  == "C2"~ "100",
                          site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt)) 

```

Cq --> Copies/mL

```{r}
copies<- filter %>%
   mutate(
   log_sq = ((Cq-36.497)/-3.166), 
   sq = 10^log_sq, 
    copies_uL = sq , 
    copies_uL= case_when((copies_uL == "NaN" | copies_uL < vp_LOD) ~ 0.5*vp_LOD, #50% LOD
                     TRUE ~ copies_uL),
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL*concentration_factor) %>%
    
select(day,copies_mL,site, copies_uL) 

```

Date Column

```{r}
date<- copies %>%
  mutate(date = case_when(day == "2"~"2022-02-16",
                         day ==  "3"~"2022-03-09",
                         day ==  "4"~"2022-04-20",
                         day ==  "511"~"2022-05-11",
                         day == "520"~"2022-05-20",
                         day ==  "524"~"2022-05-24",
                         day ==  "6"~"2022-06-13",
                         day ==  "8"~"2022-08-09",
                         day ==  "9"~"2022-09-13",
                         day == "10"~"2022-10-18",
                         day ==  "11"~"2022-11-15",
                         day == "12"~"2022-12-14"))

```

```{r}
write_csv(date,here('data', 'processed_data', 'ANOVA Data', 'vp_anova_monthly.csv' ))
```

Take the average of qPCR triplicates

```{r}
final_m<- date %>% 
  group_by(day, site,date) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() %>% #Ungroup to spit everything back out 
  select(date,copies_mL,site, copies_uL)
```

Save as RDS and manually add date in excel

```{r}
#stop() #Write error so it wont overwrite
write.csv(final_m, file= here("data","processed_data","vp_mon_clean_copies.csv"))
```

#### Combine DF

```{r}
vp_final<-
  full_join(final_d, final_m) %>%
  drop_na()

write_csv(vp_final, here('data', 'processed_data', 'qpcr', 'for_real', 'vp_final.csv'))
```
