---
title: "Vp qPCR"
format:
  html:
    theme: default
---

*This dataset is Daily Vp qPCR*

# Daily

Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
```

Load data

```{r}
sq <-read_csv(here("data", "raw_data", 'qpcr', 'vp',  "vp_daily.csv")) 
```

Filter for HEX dye (samples). Cy5 is for IAC

```{r}
sq2<- sq %>% 
  select(SQ,Cq, Sample, Fluor) %>%
  filter(Fluor %in% "HEX")

```

Create Site Column from Sample Name

```{r}
site<- sq2 %>%
  mutate(site = substr(sq2$Sample,1,2)) #Creates new column `Site` from the first two letters in `Sample` (BO16 becomes BO)
```

Add Dilution Column and Filter column

```{r}
dilution<- site%>%
  mutate(dilution = case_when(site == "BO"~"10",#BO was 1:10
                              site  == "C2"~ "1",
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution)) 


filter<- dilution %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100",
                          Sample == "BO_7"~"100",
                          Sample == "BO_8"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_11"~"100",
                          Sample == "BO_12"~"50",
                          Sample == "BO_13"~"50",
                          Sample == "BO_14"~"50",
                          Sample == "BO_15"~"50",
                          Sample == "BO_16"~"30",
                          Sample == "BO_17"~"30",
                          Sample == "BO_18"~"30",
                          Sample == "BO_19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt)) 

```

Cq --> Copies/mL

```{r}
copies<- filter %>%
   mutate(
   #log_sq = ((Cq-36.497)/-3.166), #Equation of the line to get log(SQ)
   # sq = 10^log_sq, #Unlog 
    #copies_rxn = SQ*15, #SQ*Reaction Volume
    #opies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = SQ *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%
    
select(Sample,copies_mL,site) 

```

Replace NaN with 0 for copies/mL

```{r}
replace<- copies %>% 
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(Sample))   #Dropping NAs from STD Curve 
```

Date Column

```{r}
date<- replace %>%
  mutate(day = substr(replace$Sample,4,5)) %>% #Creates new column `day` 
  mutate(date = case_when(day == "7"~"2022-07-07",
                         day ==  "8"~"2022-07-08",
                         day ==  "9"~"2022-07-09",
                         day ==  "11"~"2022-07-11",
                         day == "12"~"2022-07-12",
                         day ==  "13"~"2022-07-13",
                         day ==  "14"~"2022-07-14",
                         day ==  "15"~"2022-07-15",
                         day ==  "16"~"2022-07-16",
                         day == "17"~"2022-07-17",
                         day ==  "18"~"2022-07-18",
                         day == "19"~"2022-07-19"))

```

Take the average of qPCR triplicates

```{r}
final_d<- date %>% 
  group_by(site, Sample,date) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() %>% #Ungroup to spit everything back out 
  select(date,copies_mL,site)
```

Save as RDS and manually add date in excel

```{r}
#stop() #Write error so it wont overwrite
write.csv(final_d, file= here("data","processed_data","vp_clean_copies.csv"))
```

------------------------------------------------------------------------

# Monthly

*This dataset is Monthly Vp qPCR*

Load data

```{r}
sq <-read_csv(here("data", "raw_data", 'qpcr', 'vp', "vp_mon.csv")) 
```

Filter for HEX dye (samples). Cy5 is for IAC

```{r}
sq2<- sq %>% 
  select(SQ,Cq, site, Fluor, day) %>%
  filter(Fluor %in% "HEX")

```

Add Dilution Column and Filter column

```{r}
dilution<- sq2%>%
  mutate(dilution = case_when(site == "BO"~"1", #BO was 1:1
                              site  == "C2"~ "1",
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution)) 


filter<- dilution %>%
   mutate(filter_amt = case_when(
                          site == "BO" & day == 2 ~"100",
                          site == "BO" & day == 3 ~ "100",
                          site == "BO" & day == 4 ~ "100",
                          site == "BO" & day == 511 ~"100",
                          site == "BO" & day == 520 ~ "100",
                          site == "BO" & day == 524 ~ "100",
                          site == "BO" & day == 6 ~"100",
                          site == "BO" & day == 8~ "30",
                          site == "BO" & day == 9~"45",
                          site == "BO" & day == 10 ~ "60",
                          site == "BO" & day == 11~ "30",
                          site == "BO" & day == 12~ "60",
                          site  == "C2"~ "100",
                          site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt)) 

```

Cq --> Copies/mL

```{r}
copies<- filter %>%
   mutate(
   log_sq = ((Cq-36.497)/-3.166), #Equation of the line to get log(SQ)
   sq = 10^log_sq, #Unlog 
    #copies_rxn = sq*15, #SQ*Reaction Volume
    #copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = sq *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%
    
select(day,copies_mL,site) 

```

Replace NaN with 0 for copies/mL

```{r}
replace<- copies %>% 
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(site))   #Dropping NAs from STD Curve 
```

Date Column

```{r}
date<- replace %>%
  mutate(date = case_when(day == "2"~"2022-02-16",
                         day ==  "3"~"2022-03-09",
                         day ==  "4"~"2022-04-20",
                         day ==  "511"~"2022-05-11",
                         day == "520"~"2022-05-20",
                         day ==  "524"~"2022-05-24",
                         day ==  "6"~"2022-06-13",
                         day ==  "8"~"2022-08-09",
                         day ==  "9"~"2022-09-13",
                         day == "10"~"2022-10-18",
                         day ==  "11"~"2022-11-15",
                         day == "12"~"2022-12-14"))

```

Take the average of qPCR triplicates

```{r}
final_m<- date %>% 
  group_by(day, site,date) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() %>% #Ungroup to spit everything back out 
  select(date,copies_mL,site)
```

Save as RDS and manually add date in excel

```{r}
#stop() #Write error so it wont overwrite
write.csv(final_m, file= here("data","processed_data","vp_mon_clean_copies.csv"))
```

#### Combine DF

```{r}
vp_final<-
  full_join(final_d, final_m)

write_csv(vp_final, here('data', 'processed_data', 'qpcr', 'for_real', 'vp_final.csv'))
```
