---
title: "Vv caluclator"
format:
  html:
    theme: default
---

*This dataset is Daily/Monthly Vv qPCR*

Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
select<-dplyr::select
here<- here::here
mutate<- dplyr::mutate
```

Load data

```{r}
redo<- read_csv(here("data", "raw_data", 'qpcr','vv',"vv_daily.csv")) #Trial 2 is good Trial for daily
mon<- read_csv(here("data", "raw_data", 'qpcr','vv',"vv_mon.csv")) #Monthly
```

## Daily

Filter for HEX dye (samples). Cy5 is for IAC

```{r}
redo2<- redo %>% 
  dplyr::select(Cq, Sample, Fluor, Well) %>%
  filter(Fluor %in% "HEX",
        !Well %in% "K19") #This triplicate amplified 
```

Create Site Column from Sample Name

```{r}
site_redo<- redo2 %>%
  mutate(site = substr(redo2$Sample,1,2)) #Creates new column `Site` from the first two letters in `Sample` (BO16 becomes BO)
```

Add Dilution Column and Filter column

```{r}
dilution_redo<- site_redo%>%
  mutate(dilution = case_when(site == "BO"~"10", #BO was 1:10
                              site  == "C2"~ "1",
                              site == "RD"~"1"),
         dilution = as.numeric(dilution))



filter_redo<- dilution_redo %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100",
                          Sample == "BO_8"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_11"~"100",
                          Sample == "BO_12"~"50",
                          Sample == "BO_13"~"50",
                          Sample == "BO_14"~"50",
                          Sample == "BO_15"~"50",
                          Sample == "BO_16"~"30",
                          Sample == "BO_17"~"30",
                          Sample == "BO_18"~"30",
                          Sample == "BO_19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
          filter_amt = as.numeric(filter_amt)) 
```

Cq --> Copies/mL

```{r}
vv_LOD<- 3 #LOD copies/µL
```

```{r}

copies_redo<- filter_redo %>%
    mutate(
    log_sq = ((Cq-37.606)/-3.409), 
    sq = 10^log_sq, # 
    copies_uL = sq, 
    copies_uL= case_when((copies_uL == "NaN"| copies_uL < vv_LOD)~ 0.5*vv_LOD, #50% LOD
                     TRUE ~ copies_uL),
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL*concentration_factor*dilution) 


```

```{r}
copies_redo<-
  copies_redo %>%
dplyr::select(Sample,copies_mL, site, copies_uL)
```

Date Column

```{r}

date_redo<- copies_redo %>%
  mutate(day = substr(copies_redo$Sample,4,5)) %>% #Creates new column `date`
  mutate(date = case_when(day == "7"~"2022-07-07",
                         day ==  "8"~"2022-07-08",
                         day ==  "9"~"2022-07-09",
                         day ==  "11"~"2022-07-11",
                         day == "12"~"2022-07-12",
                         day ==  "13"~"2022-07-13",
                         day ==  "14"~"2022-07-14",
                         day ==  "15"~"2022-07-15",
                         day ==  "16"~"2022-07-16",
                         day == "17"~"2022-07-17",
                         day ==  "18"~"2022-07-18",
                         day == "19"~"2022-07-19"))


```

#### Save for ANOVA

```{r}
write_csv(date_redo, here('data', 'processed_data', 'ANOVA Data', 'vv_anova.csv'))
```

Take the average of qPCR triplicates

```{r}
final_redo<- date_redo %>% 
  group_by(site, Sample,date) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() %>% #Ungroup to spit everything back out 
  select(date,copies_mL,site, copies_uL)
```

Save as RDS and manually add date in excel

```{r}
#stop() #Write error so it wont overwrite
write.csv(final_redo, file= here("data","processed_data","vv_clean_copies_redo.csv"))
```

------------------------------------------------------------------------

## Monthly

Clean

```{r}
mon2<- mon %>% 
  select(Cq, Sample, Fluor, Well) %>%
  filter(Fluor %in% "HEX", #HEX Dye is for Vibrio
        !Well %in% "K19") %>% #This triplicate amplified 
  filter(!grepl('i', Sample)) #Gets rid of inhibition Samples 
```

Create Site Column from Sample Name

```{r}
site_mon<- mon2 %>%
  mutate(site = substr(mon2$Sample,1,2)) #Creates new column `Site` from the first two letters in `Sample` (BO16 becomes BO)
```

Add Dilution Column and Filter column

```{r}
dilution_mon<- site_mon%>%
  mutate(dilution = case_when(site == "BO"~"1", #BO was 1:1
                              site  == "C2"~ "1",
                              site == "RD"~"1"),
         dilution = as.numeric(dilution))



filter_mon<- dilution_mon %>%
   mutate(filter_amt = case_when(
                          Sample == "BO_2"~"100",
                          Sample == "BO_3"~"100",
                          Sample == "BO_4"~"100",
                          Sample == "BO_5_11"~"100",
                          Sample == "BO_5_20"~"100",
                          Sample == "BO_5_24"~"100",
                          Sample == "BO_6"~"100",
                          Sample == "BO_8"~"30",
                          Sample == "BO_9"~"45",
                          Sample == "BO_10"~"60",
                          Sample == "BO_11"~"30",
                          Sample == "BO_12"~"60",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
          filter_amt = as.numeric(filter_amt)) 
```

Cq --> Copies/mL

```{r}

copies_mon<- filter_mon %>%
    mutate(
    log_sq = ((Cq-37.606)/-3.409),
    sq = 10^log_sq, 
    copies_uL = sq , 
    copies_uL= case_when((copies_uL == "NaN"| copies_uL < vv_LOD)~ 0.5*vv_LOD, #50% LOD
                     TRUE ~ copies_uL),
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL*concentration_factor*dilution) %>%
    
select(Sample,copies_mL, site, copies_uL)


```

Date Column

```{r}
date_mon<- copies_mon %>%
  mutate(day = substr(copies_mon$Sample,4,7)) %>% #Creates new column `date`
  mutate(date = case_when(day == "2"~"2022-02-16",
                         day ==  "3"~"2022-03-09",
                         day ==  "4"~"2022-04-20",
                         day ==  "5_11"~"2022-05-11",
                         day == "5_20"~"2022-05-20",
                         day ==  "5_24"~"2022-05-24",
                         day ==  "6"~"2022-06-14",
                         day ==  "8"~"2022-08-09",
                         day ==  "9"~"2022-09-13",
                         day == "10"~"2022-10-18",
                         day ==  "11"~"2022-11-15",
                         day == "12"~"2022-12-14"))
```

```{r}
write_csv(date_mon, here('data', 'processed_data', 'ANOVA Data', 'vv_anova_monthly.csv'))
```

Take the average of qPCR triplicates

```{r}
final_mon<- date_mon %>% 
  group_by(site, Sample,date) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() %>% #Ungroup to spit everything back out 
  select(date,copies_mL,site)
```

Save as RDS and manually add date in excel

```{r}
#stop() #Write error so it wont overwrite
write.csv(final_mon, file= here("data","processed_data","vv_clean_copies_mon.csv"))
```

#### Combiune DF

```{r}
vv_final<-
  full_join(final_redo, final_mon) %>%
  filter(!site %in% c("E3", "NT")) %>%
  drop_na

write_csv(vv_final, here('data', 'processed_data', 'qpcr', 'for_real', 'vv_final.csv'))
```
