---
title: "Untitled"
format:
  html:
    theme: default
---

**This code creates a correlation matrix to look at relationships between variables. This helps identify specific relationships of interest**

[Link](http://www.sthda.com/english/wiki/correlation-matrix-a-quick-start-guide-to-analyze-format-and-visualize-a-correlation-matrix-using-r-software):

# Getting Started

#### Libraries

```{r, include= FALSE}
library(tidyverse)
library(here)
library(Hmisc)#Cor Tables and Lag
library(corrplot) #Cor Plots
library(lubridate) #For dates
library(ggpubr) #Plot stacking
library(kableExtra)
library(naniar)
library(corrtable) #This is a good package for making corrleation tables as opposed to matrices
```

#### Data

Site data sets have lags incorporated (made in `MASTER_MAKER.qmd`)

```{r, include = FALSE}
bo<- read_csv(here("data", "processed_data", "bo_master_daily.csv"))
c2<- read_csv(here("data", "processed_data", "c2_master_daily.csv"))
rd<- read_csv(here("data", "processed_data", "rd_master_daily.csv"))
sp<- read_rds(here("data", "processed_data", "qpcr", "species_copies.rds")) #species specific copiesv
```

# Cleaning

#### Remove non-numeric variables

```{r}
bo<- 
  bo %>%
  dplyr::select(!c(...1, date, Vp, cfu_gre, cfu_yel, VAI))

c2<- 
  c2 %>%
  dplyr::select(!c( ...1, date, hf_copies_mL,cfu_gre, cfu_yel, VAI))

rd<- 
  rd %>%
  dplyr::select(!c(...1, date, hf_copies_mL,cfu_gre, cfu_yel, VAI))
```

#### Rename Copies --> Vibrio

```{r}
bo<- 
  bo %>%
  rename("Total Vibrio" = "copies_mL",
         "Chlorophyl a" = "chl",
         "Salinity" = "sal",
         "Temperature" = "temp",
         "Dissolved Oxygen (mg/L)" = "do_mgl",
         "Dissolved Oxygen (%)" = "do_per",
         "Secchi" = "secchi",
         "Ammonium" = "amm",
         "Nitrate+Nitrite" = "nn",
         "Orthophosphate" = "orthop",
         "Silicate" = "sil",
         "DIN" = "din",
         "DIN:DIP" = "din_dip",
         "TDN" = "tdn",
         "DON" = "don",
         "DOC" = "doc",
         "TOC" = "toc",
         "TN" = "tn",
         "Dust" = "dust",
         "Dust_Lag" = "dust_lag",
         "Total CFU" = "cfu_tot",
         "HF183" = "hf_copies_mL",
         "Total Bacteria" = "tot_bacteria",
        # "Yellow CFU"  = "cfu_yel",
        # "Green CFU" = "cfu_gre",
         "TSS" = "tss")

c2<- 
  c2 %>%
  rename("Total Vibrio" = "copies_mL",
         "Chlorophyl a" = "chl",
         "Salinity" = "sal",
         "Temperature" = "temp",
         "Dissolved Oxygen (mg/L)" = "do_mgl",
         "Dissolved Oxygen (%)" = "do_per",
         "Secchi" = "secchi",
         "Ammonium" = "amm",
         "Nitrate+Nitrite" = "nn",
         "Orthophosphate" = "orthop",
         "Silicate" = "sil",
         "DIN" = "din",
         "DIN:DIP" = "din_dip",
         "TDN" = "tdn",
         "DON" = "don",
         "DOC" = "doc",
         "TOC" = "toc",
         "TN" = "tn",
         "Dust" = "dust",
         "Dust_Lag" = "dust_lag",
         "Total CFU" = "cfu_tot",
         "Total Bacteria" = "tot_bacteria",
       #  "Yellow CFU"  = "cfu_yel",
        # "Green CFU" = "cfu_gre",
         "TSS" = "tss")

rd<- 
  rd %>%
  rename("Total Vibrio" = "copies_mL",
         "Chlorophyl a" = "chl",
         "Salinity" = "sal",
         "Temperature" = "temp",
         "Dissolved Oxygen (mg/L)" = "do_mgl",
         "Dissolved Oxygen (%)" = "do_per",
         "Secchi" = "secchi",
         "Ammonium" = "amm",
         "Nitrate+Nitrite" = "nn",
         "Orthophosphate" = "orthop",
         "Silicate" = "sil",
         "DIN" = "din",
         "DIN:DIP" = "din_dip",
         "TDN" = "tdn",
         "DON" = "don",
         "DOC" = "doc",
         "TOC" = "toc",
         "TN" = "tn",
         "Dust" = "dust",
         "Dust_Lag" = "dust_lag",
         "Total CFU" = "cfu_tot",
         "Total Bacteria" = "tot_bacteria",
        # "Yellow CFU"  = "cfu_yel",
        # "Green CFU" = "cfu_gre",
         "TSS" = "tss")
```

# Correlation Matrix

#### Compute Matrix

```{r}
bo_cor<- rcorr(as.matrix(bo), type = "spearman")
diag(bo_cor$P) <- 0

c2_cor<- rcorr(as.matrix(c2), type = "spearman")
diag(c2_cor$P) <- 0

rd_cor<- rcorr(as.matrix(rd), type = "spearman")
diag(rd_cor$P) <- 0
```

#### Create Function to make table form of matrix

```{r}
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
```

#### Make DF of Correlations and p-values

```{r}
b<- flattenCorrMatrix(bo_cor$r, bo_cor$P)
c<- flattenCorrMatrix(c2_cor$r, c2_cor$P)
r<- flattenCorrMatrix(rd_cor$r, rd_cor$P)
```

#### Site-specific Correlation Plot

<!--# FYI: WE CAN USE PEARSON FOR LOG10(DUST) X VIBRIO -->

<!--# BUT FOR THE SAKE OF CONSISTENCY, WE WILL USE SPEARMANS FOR EVERYTHING -->

```{r, fig.width = 8, fig.height=8}
corrplot(bo_cor$r, type="upper",
         tl.col = "black",
         p.mat = bo_cor$P, sig.level = 0.05, insig = "blank",
         addCoef.col = "black",
         number.cex = 0.60,
         title = "BLIND OSO", mar = c(0,0,1,0))

corrplot(c2_cor$r, type="upper",
         tl.col = "black",
         p.mat = c2_cor$P, sig.level = 0.05, insig = "blank",
         addCoef.col = "black",
         number.cex = 0.60,
         title = "CANALS", mar = c(0,0,1,0))

corrplot(rd_cor$r, type="upper",
         tl.col = "black",
         p.mat = rd_cor$P, sig.level = 0.05, insig = "blank",
         addCoef.col = "black",
         number.cex = 0.60,
         title = "GULF", mar = c(0,0,1,0))

flattenCorrMatrix(bo_cor$r, bo_cor$P)
flattenCorrMatrix(c2_cor$r, c2_cor$P)
flattenCorrMatrix(rd_cor$r, rd_cor$P)

```

\

#### All Sites Correlation Plot

```{r}
bo<-bo %>%
  mutate(Vp = "0",
         Vp = as.numeric(Vp)) %>%
  dplyr::select(!HF183)

all<- 
  rbind(c2, rd, bo) %>%
  #Remove Non-interesting variables
  dplyr::select(!c("Dissolved Oxygen (%)", "Secchi", "DIN:DIP"))

all_cor<- rcorr(as.matrix(all), type = "spearman")
flattenCorrMatrix(all_cor$r, all_cor$P)
diag(all_cor$P) <- 0
```

```{r, fig.width=9, fig.height=9}
corrplot(all_cor$r, type="upper", 
         tl.col = "black",
         p.mat = all_cor$P, sig.level = 0.05, insig = "blank",
         addCoef.col = "black",
         number.cex = 0.60,
         title = "All Sites", mar = c(0,0,1,0)) 
```
