---
title: "New Dust and Copies"
format:
  html:
    theme: default
---

**This code is useful for looking at variations of daily dust trends. For example, when running statistical analysis, it may be best to look at dust concentration at a specific hour, or the sum per day, or the average. We will be working with a sum that is 24hr prior to sample collection. This utilizes a data set that has the variations of dust trends**

# Intro

#### Libs

```{r}
library(here)
library(tidyverse)
library(lubridate)
```

#### Data

```{r}
dust<- read_csv(here("data", "processed_data", "dust","dust_master.csv")) 
dust_all<- read_csv(here("data", "processed_data","tx_master.csv")) 
```

**There are a few columns that we do not need or that contain NaN. So let's remove those.**

# Clean

```{r}
dust<- dust %>%
  filter(between(date,as.Date('2022-07-05'), as.Date('2022-07-19')))

dust_all<- dust_all %>%
  select(date, hr_cst, Dust) %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) 

dust_all<- dust_all %>%
  mutate(ymdh = paste(dust_all$date, dust_all$hr_cst, sep = "-")) #Combines Hour and Date
  
dust_all<- dust_all %>% #Set as YMDH
  mutate(ymdh = ymd_h(dust_all$ymdh))
```

Plot T7sum

```{r}
dust %>% ggplot()+ geom_line(
  aes(x = date,
      y = t7sum))+
  labs(title = "Dust Concentration over Daily Time Series",
       x = "Date",
       y = "Dust Concentration (AOD)")+
  theme_bw()+
  scale_x_date(date_breaks = "1 day", date_labels = "%b%d")

ggsave(here("results", "plots", "dust_daily.png"))
```
