---
title: "Distriburion"
format:
  html:
    theme: default
---

# Libs/Data

#### Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
```

#### Data

```{r, include = FALSE}
d<- read_csv(here("data", "processed_data","tx_master.csv"))
dust<- read_csv(here("data", "processed_data", "dust","dust_master.csv"))
sp<- read_rds(here("data", "processed_data", "qpcr", "species_copies.rds")) #species specific copies

```

#### Clean Data

##### Meta

```{r}
d_clean<- d %>%
  filter(date %in% as.Date("2022-07-04"):as.Date("2022-07-19"),
         hr_cst %in% "01") #Just to get rid of duplicates


master<- d_clean %>%
  select(copies_mL,site, date) %>%
  filter(!is.na(site))

#Site Specific datasets
bo<- 
  master %>%
  filter(site %in% "Blind Oso")
c2<- 
  master %>%
  filter(site %in% "Canals")
rd<- 
  master %>%
  filter(site %in% "Gulf")
```

##### Dust

```{r}
#Daily df
daily<- 
  dust %>%
  filter(date %in% as.Date('2022-07-07') : as.Date('2022-07-19')) #%>%
  #mutate(t7sumlog = log10(t7sum)) #Log transform
```

# Check Distributions of Data

## Total Copies/mL

#### Visualization

**Density plot**: the **density** plot provides a visual judgment about whether the distribution is bell shaped.

```{r}
ggdensity(
  bo$copies_mL,
  main = "Blind Oso",
  xlab = "Copies per mL")

ggdensity(
  c2$copies_mL,
  main = "Canals",
  xlab = "Copies per mL")

ggdensity(
  rd$copies_mL,
  main = "Gulf",
  xlab = "Copies per mL")
```

**Q-Q plot**: **Q-Q plot** (or quantile-quantile plot) draws the correlation between a given sample and the normal distribution. A 45-degree reference line is also plotted.

```{r}
ggqqplot(bo$copies_mL)

ggqqplot(c2$copies_mL)

ggqqplot(rd$copies_mL)
```

### Normality Test

**Shapiro-Wilk's method** is widely recommended for normality test and it provides better power than K-S. It is based on the correlation between the data and the corresponding normal scores.

-   Note that, normality test is sensitive to sample size. Small samples most often pass normality tests. Therefore, it's important to combine visual inspection and significance test in order to take the right decision.

    ```{r}
    shapiro.test(bo$copies_mL)
    shapiro.test(c2$copies_mL)
    shapiro.test(rd$copies_mL)
    ```

    A p-value > 0.05 implies that the distribution of the data is **not significantly differen**t from normal distribution. In other words, **we can assume the normality for copies_mL at all sites.**

## Dust

### Normality Test

```{r}
daily<- 
  daily %>%
  select(!date)

apply(daily,2,shapiro.test) #Number '2' indicates columns. '1' would be rows.
```

**All of our dust permutations are not normally distributed. So let's log transform and run the test again.**

#### Log transform data

```{r}
log_daily<- 
  daily %>%
  mutate(
    t1 = log10(t1),
    t7 = log10(t7),
    t13 = log10(t13),
    t19 = log10(t19),
    tsum = log10(tsum),
    tavg = log10(tavg),
    t7sum = log10(t7sum),
    t7avg = log10(t7avg),
  )
```

#### Re-run Normality test on new log data

```{r}
apply(log_daily,2,shapiro.test) 
```

**All look good except t19.**

## Species-specific Distributions

#### Make site and sp df

```{r}
#BLIND OSO
b_vc<- 
  sp %>%
  filter(site %in% "Blind Oso" & type %in% "V. cholerae")

b_vv<- 
  sp %>%
  filter(site %in% "Blind Oso" & type %in% "V. vulnificus")

#b_vp = 0 

#CANALS
c_vc<- 
  sp %>%
  filter(site %in% "Canals" & type %in% "V. cholerae")

c_vv<- 
  sp %>%
  filter(site %in% "Canals" & type %in% "V. vulnificus")

c_vp<- 
  sp %>%
  filter(site %in% "Canals" & type %in% "V. parahaemolyticus")

#GULF
r_vc<- 
  sp %>%
  filter(site %in% "Gulf" & type %in% "V. cholerae")

r_vv<- 
  sp %>%
  filter(site %in% "Gulf" & type %in% "V. vulnificus")

r_vp<- 
  sp %>%
  filter(site %in% "Gulf" & type %in% "V. parahaemolyticus")
```

#### Shapiro Test

```{r}
#BLIND OSO
shapiro.test(b_vc$copies_mL)
shapiro.test(b_vv$copies_mL)

#CANALS
shapiro.test(c_vc$copies_mL)
shapiro.test(c_vv$copies_mL)
shapiro.test(c_vp$copies_mL)

#GULF
shapiro.test(c_vc$copies_mL)
shapiro.test(c_vv$copies_mL)
shapiro.test(c_vp$copies_mL)
```

#### Log-transform

```{r}

```
