---
title: "roc"
format:
  html:
    theme: default
---

### Libraries

```{r}
library(tidyverse)
library(here)
```

# LOADING AND CLEANING DATA

### Data

```{r}
dust<- read_csv(here("data", "processed_data","dust_conc", "dust_master.csv")) #Different Dust attributes
master<- read_csv(here("data", "processed_data", "tx_master.csv")) #Master Data
```

### Daily and Monthly Dataframe

```{r}
daily <- 
  master %>%
  filter(date %in% as.Date('2022-07-07') : as.Date('2022-07-19'), #Daily Time series
         hr_cst %in% "01", #gets rid of reps
         !date %in% as.Date('2022-07-10')) %>% #Gets rid of 7/10 as no samples collected then
  left_join(dust) %>%
   select(date, copies_mL, site, t7sum)

mon<- 
  master %>%
  filter(Type %in% "Monthly",
         hr_cst ==  "01" | #gets rid of reps for copies_mL
         hr_cst =="00" |
         date %in% as.Date('2022-09-13'): as.Date("2022-12-14")) %>%
  select(date, copies_mL, site)
```

### Site DF

```{r}
#Daily Sites
bo_d<- 
  daily %>%
  filter(site %in% "Blind Oso")

c2_d<- 
  daily %>%
  filter(site %in% "Canals")

rd_d<- 
  daily %>%
  filter(site %in% "Gulf")

#Monthly Sites

bo_m<- 
  mon %>%
  filter(site %in% "Blind Oso")

c2_m<- 
  mon %>%
  filter(site %in% "Canals")

rd_m<- 
  mon %>%
  filter(site %in% "Gulf")
```

### Find Site average copies/mL over the year

```{r}
bo_avg<- 
  mean(bo_m$copies_mL)

c2_avg<- 
  mean(c2_m$copies_mL)

rd_avg<- 
  mean(rd_m$copies_mL)
```

+-------------+-------------------+
| Site        | Average copies_mL |
+=============+===================+
| Blind Oso   | 24260.4573632452  |
+-------------+-------------------+
| Canals      | 7739.38371599866  |
+-------------+-------------------+
| Gulf        | 23116.2579088854  |
+-------------+-------------------+

### Make Rate of change column

We do this by taking the measured copies_mL and dividing by the yearly average. Then we find the difference between ROC value and the average

```{r}
bo_d<- 
  bo_d %>%
  mutate(
    roc = copies_mL / bo_avg, #rate of change
    dif = roc - 1) #difference between roc and average (1)

c2_d<- 
  c2_d %>%
  mutate(
    roc = copies_mL / c2_avg,
    dif = roc - 1)

rd_d<- 
  rd_d %>%
  mutate(
    roc = copies_mL / rd_avg,
    dif = roc - 1)
```

### Plot rate of change for each site

```{r}
bo_d %>%
  ggplot() +geom_line(
    aes(
      x = date,
      y = roc)) +
  geom_hline(yintercept  = 1)
    
c2_d %>%
  ggplot() +geom_line(
    aes(
      x = date,
      y = roc))+
  geom_hline(yintercept  = 1)

rd_d %>%
  ggplot() +geom_line(
    aes(
      x = date,
      y = roc))+
  geom_hline(yintercept  = 1)
```
