---
title: "Environmental Parameters"
format:
  html:
    theme: default
---

**This data set contains environmental parameters: Temp and Salinity, among other environmental parameters.**

# Getting Started

#### Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
library(lubridate)
library(Rmisc)#For stat summary
```

#### Load Data

```{r}
here<- here::here
select<-dplyr::select
```

```{r}
d1<- read_csv(here("data", "processed_data", "tx_master.csv"))
env<- read_csv(here("data", "processed_data", "env", "ENV_REPS.csv"))
bac<-read_csv(here('data', 'processed_data', 'ANOVA Data', 'total_bacteria.csv'))



```

# Cleaning

#### Daily data frame

```{r}
daily<- d1 %>%
  filter(date %in% c(as.Date("2022-07-07"):as.Date("2022-07-19"))) %>%
  filter(!date %in% as.Date('2022-07-10')) %>%
  dplyr::select(!...1)
```

#### Meta Data

```{r}
env_meta_daily<- 
  env %>%
  dplyr::select(Date, Site, Water_depth) %>%
  filter(between(Date, as.Date('2022-07-07'), as.Date("2022-07-19")),
         !grepl('-', Water_depth)) %>%
  unique() %>%
  drop_na() %>%
  mutate(Water_depth = as.numeric(Water_depth))
```

# Visualization

## YSI (1 Rep)

#### Temperature

```{r}
cbbPalette <- c("#DDAA33", "#BB5566", "#004488")
```

```{r}
temp<- 
  daily %>% 
  ggplot() + 
 # geom_point(
 # aes(
  #  x = date,
  #  y = temp,
  #  color = site),
 # size = 2)+
  geom_line(
  aes(
    x = date,
    y = temp,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Temperature (°C)",
   # title = "Daily Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 13, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.position = "none") + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)

ggsave(here("results", "plots", "env", "temp.png"))
```

#### Salinity

```{r}
sal<- daily %>% 
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = sal,
    color = site),
  size = 1)+
  #geom_point(
 # aes(
  #  x = date,
  #  y = sal,
  #  color = site),
  #size = 2)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Salinity",
    #title = "Daily Salinities",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
   # axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 13, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.position = "none") + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)
```

#### pH 

```{r}
pH<-
  daily %>%
  ggplot() + geom_line(
  aes(
    x = date,
    y = pH,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "pH",
  #  title = "Temperature across Daily Time Series by Site",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(size = 7, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)

```

#### Secchi

```{r}
secchi<-
  daily %>%
  ggplot() + geom_line(
  aes(
    x = date,
    y = secchi,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Secchi Depth (m)",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 7, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.key.size = unit(0.3,'cm'),
    legend.position = "none")+
    scale_color_manual(values = cbbPalette)

```

#### Dissolved Oxygen

```{r}
do<-
  daily %>%
  ggplot() + geom_line(
  aes(
    x = date,
    y = do_mgl,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "DO (mg/L)",
  #  title = "Temperature across Daily Time Series by Site",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 13, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)

```

## NUTRIENTS (2 Reps)

#### Nitrite:Nitrate

```{r}
nn_sum <- summarySE(env, measurevar="NO2NO3", groupvars=c("Site", "Date")) 

nn<-
  ggplot(nn_sum, 
       aes(x=Date, 
           y=NO2NO3, 
           color=Site)) + 
    geom_errorbar(data = nn_sum,
      aes(ymin=NO2NO3-se, 
          ymax=NO2NO3+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = nn_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "NO3- + NO2- (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### Orthophosphate

```{r}
po_sum <- summarySE(env, measurevar="Orthophosphate", groupvars=c("Site", "Date")) 

ortho<-
  ggplot(po_sum, 
       aes(x=Date, 
           y=Orthophosphate, 
           color=Site)) + 
    geom_errorbar(data = po_sum,
      aes(ymin=Orthophosphate-se, 
          ymax=Orthophosphate+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = po_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "O-phosphate (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### DON (TDN - NN - Amm)

```{r}
don_sum <- summarySE(env, measurevar="DON", groupvars=c("Site", "Date")) 

don<-
  ggplot(don_sum, 
       aes(x=Date, 
           y=DON, 
           color=Site)) + 
    geom_errorbar(data = don_sum,
      aes(ymin=DON-se, 
          ymax=DON+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = don_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "DON (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### DOC

```{r}
doc_sum <- summarySE(env, measurevar="DOC", groupvars=c("Site", "Date")) 

doc<-
  ggplot(doc_sum, 
       aes(x=Date, 
           y=DOC, 
           color=Site)) + 
    geom_errorbar(data = doc_sum,
      aes(ymin=DOC-se, 
          ymax=DOC+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = doc_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "DOC (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none")  
```

#### TOC

```{r}
toc_sum <- summarySE(env, measurevar="TOC", groupvars=c("Site", "Date")) 

toc<-
  ggplot(toc_sum, 
       aes(x=Date, 
           y=TOC, 
           color=Site)) + 
    geom_errorbar(data = toc_sum,
      aes(ymin=TOC-se, 
          ymax=TOC+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = toc_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "TOC (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### 

#### Ammonium

```{r}
amm_sum <- summarySE(env, measurevar="Ammonium", groupvars=c("Site", "Date")) 

amm<-
  ggplot(amm_sum, 
       aes(x=Date, 
           y=Ammonium, 
           color=Site)) + 
    geom_errorbar(data = amm_sum,
      aes(ymin=Ammonium-se, 
          ymax=Ammonium+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = amm_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "NH4+ (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### Total Nitrogen

```{r}
tn_sum <- summarySE(env, measurevar="TN", groupvars=c("Site", "Date")) 

tn<-
  ggplot(tn_sum, 
       aes(x=Date, 
           y=TN, 
           color=Site)) + 
    geom_errorbar(data = tn_sum,
      aes(ymin=TN-se, 
          ymax=TN+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = tn_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "TN (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### Silicate

```{r}
sil_sum <- summarySE(env, measurevar="Silicate", groupvars=c("Site", "Date")) 

sil<-
  ggplot(sil_sum, 
       aes(x=Date, 
           y=Silicate, 
           color=Site)) + 
    geom_errorbar(data = sil_sum,
      aes(ymin=Silicate-se, 
          ymax=Silicate+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = sil_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "Silicate (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_text(size =10),
        axis.title.x = element_text(size = 13),
        axis.title.y = element_text(size = 13,face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### TDN

```{r}
tdn_sum <- summarySE(env, measurevar="TDN", groupvars=c("Site", "Date")) 

tdn<-
  ggplot(tdn_sum, 
       aes(x=Date, 
           y=TDN, 
           color=Site)) + 
    geom_errorbar(data = tdn_sum,
      aes(ymin=TDN-se, 
          ymax=TDN+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = tdn_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "TDN (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### DIN:DIP ((Amm + NN / Ortho))

```{r}
din_dip_sum <- summarySE(env, measurevar="DIN_DIP", groupvars=c("Site", "Date")) 

din_dip<-
  ggplot(din_dip_sum, 
       aes(x=Date, 
           y=DIN_DIP, 
           color=Site)) + 
    geom_errorbar(data = din_dip_sum,
      aes(ymin=DIN_DIP-se, 
          ymax=DIN_DIP+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = din_dip_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "DIN_DIP (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_text(size =10),
        axis.title.x = element_text(size = 13),
        axis.title.y = element_text(size = 13,face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") +
  geom_hline(yintercept = 16, linetype = "dotdash")



```

#### DIN (Amm+NN)

```{r}
din_sum <- summarySE(env, measurevar="DIN", groupvars=c("Site", "Date")) 

din<-
  ggplot(din_sum, 
       aes(x=Date, 
           y=DIN, 
           color=Site)) + 
    geom_errorbar(data = din_sum,
      aes(ymin=DIN-se, 
          ymax=DIN+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = din_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "DIN (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

## BIOTIC 

#### TOtal Bacteria

```{r}
bact<-
bac %>%
  ggplot()+
  geom_boxplot(
    aes(x = date,
        y = log10(copies_mL),
        color = site,
        group = interaction(site,date)),
    position = "identity")+
  scale_color_manual(values = cbbPalette) +
stat_summary(fun=mean, geom="line", 
             aes(x = date, 
                 y = log10(copies_mL),
                 group=site, 
                 color = site)) +
  theme_bw()+
  labs(x = "Date",
       y = "Total Bacteria (copies/mL)",
       color = "Site",
       caption = "Data is on a log-scale")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d") +
  theme(axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x =element_blank(),
        #axis.title.y = element_text(face= "bold"),
        legend.position = "none")

```

#### Chlorophyll

```{r}
chl_sum <- summarySE(env, measurevar="Chl_a", groupvars=c("Site", "Date")) 

chl<-
  ggplot(chl_sum, 
       aes(x=Date, 
           y=Chl_a, 
           color=Site)) + 
    geom_errorbar(data = chl_sum,
      aes(ymin=Chl_a-se, 
          ymax=Chl_a+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = chl_sum)+
  theme_bw()+
  labs(x = "Date",
       y = "Chl-a (mg/L)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(#axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
  
chl
```

#### TSS

```{r}
tss<-
  daily %>%
  ggplot() + geom_line(
  aes(
    x = date,
    y = tss,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "TSS (mg/L)",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
   axis.text.x = element_blank(),
    axis.title.y = element_text(size = 13, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.key.size = unit(0.3,'cm'),
    legend.position = "none")+
    scale_color_manual(values = cbbPalette)

```

#### Vibrio Copies/mL

```{r}
cop<-
  daily %>%
  
#LINE PLOT
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  
#POINT PLOT
  geom_point(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 2)+
  theme_bw()+
  
#AESTHETICS
  labs(
    x = "Date",
    y = "Copies/mL",
   # title = "Daily Total Vibrio",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 7, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.key.size = unit(0.5,'cm'),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid'),
    legend.text = element_text(size = 10)) + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)
  # annotate("text", x = as.Date('2022-07-09'), y = 115000, label = "r = 0.70", color = "#809C52") + #BO
   #annotate("text", x = as.Date('2022-07-09'), y = 100100, label = "r = 0.75", color = "#ba4716") + #C2
   #annotate("text", x = as.Date('2022-07-09'), y = 85000, label = "r = 0.67", color = "4c848c") #RD

ggsave(here("results", "plots", "env", "total_vib.png"))
```

# COMBINE

## Temp/Sal

```{r}
fig<- ggarrange(temp,
                sal+
                #nn,
                #ortho,
                #amm,
                #din,
                #don,
                #doc,
                #toc+
                #pH,
                #tss,
                #tn,
                #sil,
                #cop,
                #tdn,
               # do+
                #secchi,
                #din_dip,
                #chl+
                font("x.text", size = 8.5),
                ncol = 1, 
                nrow = 2,
                align = "v",
                common.legend  = TRUE)

fig


```

## Chl/Bact

```{r}
CHLBAC<-
  ggarrange(bact, chl +font("x.text", size = 8.5),
          nrow = 2,
          ncol = 1,
          align = "v",
          common.legend = TRUE)

annotate_figure(CHLBAC,
               bottom = text_grob("Total Bacteria is on a log-scale",
                                  hjust = 1.2, x = 1, face = "bold", size = 7))
```

# TSS, DO

```{r}
fig<- ggarrange(#temp,
                #sal+
                #nn,
                #ortho,
                #amm,
                #din,
                #don,
                #doc,
                tss,
                #toc+
                #pH,
                #tn,
                #sil,
                #cop,
                #tdn,
                do+
                #secchi,
                #din_dip,
                #chl+
                font("x.text", size = 8.5),
                ncol = 1, 
                nrow = 2,
                align = "v",
                common.legend  = TRUE)

fig

```

# P and C

```{r, fig.width=3, fig.height=3.5}
  ggarrange(ortho, doc, toc +font("x.text", size = 8.5),
          nrow = 3,
          ncol = 1,
          align = "v",
          common.legend = TRUE)
```

# Nitrate

```{r}
NITRATE<-
  ggarrange(nn,don,amm, tdn, 
          din +font("x.text", size = 8.5),
          tn+font("x.text", size = 8.5),
          nrow = 3,
          ncol = 2,
          align = "v",
          common.legend = TRUE)

annotate_figure(NITRATE,
               bottom = text_grob("DIN = NH4+ + NO3- + NO2- ; DON = TDN - DIN",
                                  hjust = 1.2, x = 1, face = "bold", size = 7))
               
```

# Redfield

```{r}
 ggarrange(din, ortho, din_dip +font("x.text", size = 8.5),
          nrow = 3,
          ncol = 1,
          align = "v",
          common.legend = TRUE)
```

# Make clean datatable for writing

```{r}
daily_clean<-
  daily %>%
  filter(hr_cst %in% "01") 
```

```{r}
single<-
  daily_clean %>%
  dplyr::select(date, site,
         orthop)

```

```{r}
g<-
  single %>%
  filter(site %in% "Gulf")

c<-
  single %>%
  filter(site %in% "Canals")

b<-
  single %>%
  filter(site %in% "Blind Oso")
```

```{r}
mean(b$orthop)
mean(c$orthop)
mean(g$orthop)
```

# 
