---
title: "Environmental Parameters"
format:
  html:
    theme: default
---

*This dataset contains environmental parameters: Temp, SAL, Nutrients*

# Getting Started

#### Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
library(lubridate)
library(kableExtra) #Tables
```

#### Data

```{r}
d1<- read_csv(here("data", "processed_data", "tx_master.csv"))
```

# Cleaning

#### Daily and Monthly data frames

```{r}
daily<- d1 %>%
  filter(Type %in% "Daily")

monthly<- d1 %>% 
  mutate(Type = case_when(d1$date == "2022-07-07"  ~ "Monthly", #This makes 7-7-22 a monthly value for July
                          d1$Type == "Monthly" ~ "Monthly")) %>%
  filter(Type %in% "Monthly") 
```

# Plots

#### Temperature

```{r}
temp<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = temp,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = temp,
    color = site),
  size = 1)+
  theme_bw()+
  #facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Temperature (°C)",
    title = "Monthly Temperature and Salinity",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")


temp
  
```

#### Salinity

```{r}
sal<-  monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = sal,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = sal,
    color = site),
  size = 1)+
  theme_bw()+
  #facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Salinity",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    #axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")


sal
```

#### Total Vibrio

```{r}
fig3 <- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Vibrio gene copies/mL",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

fig3
```

##### Combine Temp and Salinity Monthly

```{r, fig.width=3.5, fig.height=3.5}
figp<- ggarrange(temp,sal, fig3 + font("x.text", size = 10), ncol = 1, nrow = 3,align = "v")

figp
```

#### Ammonium

```{r}
amm<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Ammonium (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
amm
```

#### Chlorophyl

```{r}
chl<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = chl,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = chl,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Chlorophyl (µg/L)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
   # axis.ticks.x = element_blank(),
    axis.text.x = element_text(hjust = 1, angle = 45),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
chl
```

#### DO (mg/L)

```{r}
do_mgl<-monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = do_mgl,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = do_mgl,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "DO (mg/L)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
   # axis.ticks.x = element_blank(),
    axis.text.x = element_text(hjust = 1, angle = 45),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
do_mgl
```

#### DO (%)

```{r}
do_per<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = do_per,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = do_per,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Dissolved Oxygen (%)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
do_per
```

#### pH

```{r}
ph<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = pH,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = pH,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "pH",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
ph
```

#### Secchi

```{r}
secchi<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = secchi,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = secchi,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Secchi Depth (m)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

secchi
```

#### N+N

```{r}
nn<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = nn,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = nn,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Nitrate+Nitrite (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

nn
```

#### Orthophosphate

```{r}
orthop<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = orthop,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = orthop,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Orthophosphate (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
orthop
```

#### Silicate

```{r}
sil<-monthly %>% 
  filter(site %in% "Canals") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = sil,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = sil,
    color = site))+
  theme_bw()+
  #facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Silicate (µM)",
    title = "Canals: Silicate",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
   # axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    #axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

sil
```

#### DIN

```{r}
din<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = din,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = din,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "DIN (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
din
```

#### DIN:DIP

```{r}
din_dip<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = din_dip,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = din_dip,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "DIN:DIP (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

din_dip
```

#### TDN

```{r}
tdn<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = tdn,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = tdn,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "TDN (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

tdn
```

#### DON

```{r}
don<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = don,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = don,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "DON (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
don
```

#### DOC

```{r}
doc<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = doc,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = doc,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "DOC (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
doc
```

#### TOC

```{r}
toc<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = toc,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = toc,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "TOC (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
toc
```

#### TN

```{r}
tn<- monthly %>% ggplot() + 
  geom_point(
  aes(
    x = date,
    y = tn,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = tn,
    color = site),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "TN (µM)",
   # title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
tn
```

# ALL

```{r}
final<- ggarrange(
                temp,
                sal,
                #nn,
                #orthop,
                #amm,
                #din,
                #don,
                #doc,
               # toc,
                #pH,
               # tn,
                #sil,
               # cop,
                #tdn,
                #do_mgl,
                #secchi,
                #din_dip,
                #chl,
                #font("x.text", size = 8.5),
                ncol = 1, 
                nrow = 2,
                align = "v")

final

ggsave(here("results", "plots", "env_monthly.png"))
```

# Monthly Averages

We are taking out 5/20 and 5/24 here.

#### Make New Site-specific Data sets

<!--# This master dataset has multiple tim points. I need to just get averages from envirionmental data with one entry per date -->

```{r}
avg<- 
  monthly %>%
  filter(!date == as.Date('2022-05-24') & !date == as.Date('2022-05-20'),#Gets ride of extra dates in May
         hr_cst %in% "01" 
         | hr_cst %in% "00") 

b_avg<-
  avg %>%
  filter(site %in% "Blind Oso") %>%
  select(!c(site, date, Type, hr_cst)) 
b_avg<-
  rbind(b_avg, sapply(b_avg, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else ""))



c_avg<-
  avg %>%
  filter(site %in% "Canals")%>%
  select(!c(site, date, Type, hr_cst))
c_avg<-
  rbind(c_avg, sapply(c_avg, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else "")) 

r_avg<-
  avg %>%
  filter(site %in% "Gulf")%>%
  select(!c(site, date, Type, hr_cst))
r_avg<-
  rbind(r_avg, sapply(r_avg, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else ""))

```

#### Extract Average Values

```{r}
b_nn<- b_avg$nn[12] 
b_orthop<- b_avg$orthop[12]
b_amm<- b_avg$amm[12]

c_nn<- c_avg$nn[12]
c_orthop<- c_avg$orthop[12]
c_amm<- c_avg$amm[12]

r_nn<- r_avg$nn[12]
r_orthop<- r_avg$orthop[12]
r_amm<- r_avg$amm[12]

#DF
average_df<- 
  tibble(Site  = c("Blind Oso", "Canals", "Gulf"),
             NN = c(b_nn, c_nn, r_nn),
             OrthoP = c(b_orthop, c_orthop, r_orthop),
             Amm = c(b_amm, c_amm, r_amm))
kable(average_df)
```

#### 
