---
title: "Environmental Parameters"
format:
  html:
    theme: default
---

**This data set contains environmental parameters: Temp and Salinity, among other environmental parameters.**

# Getting Started

#### Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
library(lubridate)
library(Rmisc)#For stat summary
```

#### Load Data

```{r}
here<- here::here
select<-dplyr::select
rename<- dplyr::rename
```

```{r}
d1<- read_csv(here("data", "processed_data", "tx_master.csv"))
env<- read_csv(here("data", "processed_data", "env", "ENV_META_REPS.csv"))
ysi<- read_csv(here("data", "processed_data", "env", "ENV_META_AVG.csv"))
bac<-read_csv(here('data', 'processed_data', 'ANOVA Data', 'total_bacteria.csv'))
copies<- read_csv(here("data", "processed_data",  "ANOVA Data", "daily_anova_data.csv"))
dust<- read_csv(here("data", "processed_data", "dust", "dust_master.csv"))
vc<- read_csv(here('data', 'processed_data', 'ANOVA Data', 'vc_anova.csv'))
vc1<- read_csv(here('data', 'processed_data', 'qpcr', 'LOD', 'vc_above_below.csv'))
vv<- read_csv(here('data', 'processed_data', 'ANOVA Data', 'vv_anova.csv'))
vv1<- read_csv(here('data', 'processed_data', 'qpcr', 'LOD', 'vv_above_below.csv'))
```

# Cleaning

#### Daily data frame

```{r}
ysi<-
  ysi %>%
  filter(date %in% c(as.Date("2022-07-07"):as.Date("2022-07-19")))%>%
  mutate(site = recode(site, "BO" = "Blind Oso",
                       "C2" = "Canals",
                       "RD" = "Gulf")) %>%
  rename("Site" = "site") %>%
  filter(Site %in% "Gulf")

env<-
  env %>%
  filter(date %in% c(as.Date("2022-07-07"):as.Date("2022-07-19"))) %>%
  mutate(site = recode(site, "BO" = "Blind Oso",
                       "C2" = "Canals",
                       "RD" = "Gulf")) %>%
  rename("Site" = "site" )%>%
  filter(Site %in% "Gulf")

  
daily<-
  d1 %>%
  filter(date %in% c(as.Date("2022-07-07"):as.Date("2022-07-19")),
         hr_cst %in% "01",
         !date %in% as.Date('2022-07-10')) %>%
  rename("Site" = "site") %>%
  filter(Site %in% "Gulf")

  copies<-
  copies %>%
  filter(date %in% c(as.Date("2022-07-07"):as.Date("2022-07-19")), 
         !date %in% as.Date('2022-07-10')) %>%
  mutate(site = recode(site, "BO" = "Blind Oso",
                       "C2" = "Canals",
                       "RD" = "Gulf")) %>%
  rename("Site" = "site") %>%
  filter(Site %in% "Gulf")
  
bac<-
  bac %>%
  mutate(site = recode(site, "BO" = "Blind Oso",
                       "C2" = "Canals",
                       "RD" = "Gulf")) %>%
  rename("Site" = "site") %>%
  filter(Site %in% "Gulf")

dust<-
  dust %>%
  filter(date %in% c(as.Date("2022-07-07"):as.Date("2022-07-19")))

vc<-
  vc %>%
  select(copies_mL, date, site)%>%
  mutate(date = as.Date(date),
         site = recode(site, "BO" = "Blind Oso",
                       "C2" = "Canals",
                       "RD" = "Gulf"))
vc_sum <- summarySE(vc, measurevar="copies_mL", groupvars=c("site", "date"))
vc_sum<-
  vc_sum %>%full_join(vc1)

vv<-
  vv %>%
  select(date, copies_mL, site) %>%
  drop_na()%>%
  mutate(date = as.Date(date),
         site = recode(site, "BO" = "Blind Oso",
                       "C2" = "Canals",
                       "RD" = "Gulf"))
vv_sum <- summarySE(vv, measurevar="copies_mL", groupvars=c("site", "date"))
vv_sum<-
  vv_sum %>%full_join(vv1)
```

# Visualization

## YSI (1 Rep)

#### Temperature

```{r}
cbbPalette <- c(
  
 #"#DDAA33")
               # "#BB5566") 
  "#004488")
```

```{r}
temp<- 
  ysi %>% 
  ggplot() + 
 # geom_point(
 # aes(
  #  x = date,
  #  y = temp,
  #  color = Site),
 # size = 2)+
  geom_line(
  aes(
    x = date,
    y = Temperature,
    color = Site),
  size = 1)+
  theme_bw()+
  labs(
    x = "date",
    y = "Temperature (°C)",
   # title = "Daily Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 13, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.position = "none") + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)
temp

ggsave(here("results", "plots", "env", "temp.png"))
```

#### Salinity

```{r}
sal<- ysi %>% 
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = Salinity,
    color = Site),
  size = 1)+
  #geom_point(
 # aes(
  #  x = date,
  #  y = sal,
  #  color = Site),
  #size = 2)+
  theme_bw()+
  labs(
    x = "date",
    y = "Salinity",
    #title = "Daily Salinities",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 13, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.position = "none") + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")
sal
```

#### pH

```{r}
pH<-
  ysi %>%
  ggplot() + geom_line(
  aes(
    x = date,
    y = pH,
    color = Site),
  size = 1)+
  theme_bw()+
  labs(
    x = "date",
    y = "pH",
  #  title = "Temperature across Daily Time Series by Site",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(size = 7, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)

```

#### 

#### Dissolved Oxygen

```{r}
do<-
  ysi %>%
  ggplot() + geom_line(
  aes(
    x = date,
    y = DO_mgL,
    color = Site),
  size = 1)+
  theme_bw()+
  labs(
    x = "date",
    y = "DO (mg/L)",
  #  title = "Temperature across Daily Time Series by Site",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 13, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = cbbPalette)
do
```

## NUTRIENTS (2 Reps)

#### Nitrite:Nitrate

```{r}
nn_sum <- summarySE(env, measurevar="NO2NO3", groupvars=c("Site", "date")) 

nn<-
  ggplot(nn_sum, 
       aes(x=date, 
           y=NO2NO3, 
           color=Site)) + 
    geom_errorbar(data = nn_sum,
      aes(ymin=NO2NO3-se, 
          ymax=NO2NO3+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = nn_sum)+
  theme_bw()+
  labs(x = "date",
       y = "NO3- + NO2- (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
nn
```

#### Orthophosphate

```{r}
po_sum <- summarySE(env, measurevar="Orthophosphate", groupvars=c("Site", "date"))
ortho<-
  ggplot(po_sum, 
       aes(x=date, 
           y=Orthophosphate, 
           color=Site)) + 
    geom_errorbar(data = po_sum,
      aes(ymin=Orthophosphate-se, 
          ymax=Orthophosphate+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = po_sum)+
  theme_bw()+
  labs(x = "date",
       y = "O-phosphate (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
ortho
```

#### DON (TDN - NN - Amm)

```{r}
don_sum <- summarySE(env, measurevar="DON", groupvars=c("Site", "date"))

don<-
  ggplot(don_sum, 
       aes(x=date, 
           y=DON, 
           color=Site)) + 
    geom_errorbar(data = don_sum,
      aes(ymin=DON-se, 
          ymax=DON+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = don_sum)+
  theme_bw()+
  labs(x = "date",
       y = "DON (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
       # axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
don
```

#### DOC

```{r}
doc_sum <- summarySE(env, measurevar="DOC", groupvars=c("Site", "date"))

doc<-
  ggplot(doc_sum, 
       aes(x=date, 
           y=DOC, 
           color=Site)) + 
    geom_errorbar(data = doc_sum,
      aes(ymin=DOC-se, 
          ymax=DOC+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = doc_sum)+
  theme_bw()+
  labs(x = "date",
       y = "DOC (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none")  
```

#### TOC

```{r}
toc_sum <- summarySE(env, measurevar="TOC", groupvars=c("Site", "date")) 

toc<-
  ggplot(toc_sum, 
       aes(x=date, 
           y=TOC, 
           color=Site)) + 
    geom_errorbar(data = toc_sum,
      aes(ymin=TOC-se, 
          ymax=TOC+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = toc_sum)+
  theme_bw()+
  labs(x = "date",
       y = "TOC (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 

toc

```

#### 

#### Ammonium

```{r}
amm_sum <- summarySE(env, measurevar="Ammonium", groupvars=c("Site", "date")) 

amm<-
  ggplot(amm_sum, 
       aes(x=date, 
           y=Ammonium, 
           color=Site)) + 
    geom_errorbar(data = amm_sum,
      aes(ymin=Ammonium-se, 
          ymax=Ammonium+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = amm_sum)+
  theme_bw()+
  labs(x = "date",
       y = "NH4+ (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
amm
```

#### Total Nitrogen

```{r}
tn_sum <- summarySE(env, measurevar="TN", groupvars=c("Site", "date")) 

tn<-
  ggplot(tn_sum, 
       aes(x=date, 
           y=TN, 
           color=Site)) + 
    geom_errorbar(data = tn_sum,
      aes(ymin=TN-se, 
          ymax=TN+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = tn_sum)+
  theme_bw()+
  labs(x = "date",
       y = "TN (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 

tn
```

#### Silicate

```{r}
sil_sum <- summarySE(env, measurevar="Silicate", groupvars=c("Site", "date")) 

sil<-
  ggplot(sil_sum, 
       aes(x=date, 
           y=Silicate, 
           color=Site)) + 
    geom_errorbar(data = sil_sum,
      aes(ymin=Silicate-se, 
          ymax=Silicate+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = sil_sum)+
  theme_bw()+
  labs(x = "date",
       y = "Silicate (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_text(size =10),
        axis.title.x = element_text(size = 13),
        axis.title.y = element_text(size = 13,face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### TDN

```{r}
tdn_sum <- summarySE(env, measurevar="TDN", groupvars=c("Site", "date")) 

tdn<-
  ggplot(tdn_sum, 
       aes(x=date, 
           y=TDN, 
           color=Site)) + 
    geom_errorbar(data = tdn_sum,
      aes(ymin=TDN-se, 
          ymax=TDN+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = tdn_sum)+
  theme_bw()+
  labs(x = "date",
       y = "TDN (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
tdn
```

#### DIN:DIP ((Amm + NN / Ortho))

```{r}
din_dip_sum <- summarySE(env, measurevar="DIN_DIP", groupvars=c("Site", "date")) 

din_dip<-
  ggplot(din_dip_sum, 
       aes(x=date, 
           y=DIN_DIP, 
           color=Site)) + 
    geom_errorbar(data = din_dip_sum,
      aes(ymin=DIN_DIP-se, 
          ymax=DIN_DIP+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = din_dip_sum)+
  theme_bw()+
  labs(x = "date",
       y = "DIN_DIP (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_text(size =10),
        axis.title.x = element_text(size = 13),
        axis.title.y = element_text(size = 13,face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") +
  geom_hline(yintercept = 16, linetype = "dotdash")



```

#### DIN (Amm+NN)

```{r}
din_sum <- summarySE(env, measurevar="DIN", groupvars=c("Site", "date")) 

din<-
  ggplot(din_sum, 
       aes(x=date, 
           y=DIN, 
           color=Site)) + 
    geom_errorbar(data = din_sum,
      aes(ymin=DIN-se, 
          ymax=DIN+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = din_sum)+
  theme_bw()+
  labs(x = "date",
       y = "DIN (µM)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
```

#### Dust

```{r}
dus<-
dust %>%
  ggplot()+
  geom_boxplot(
    aes(x = date,
        y = t7sum,
       group = interaction(date),
    position = "identity"),
        size = 0)+
  scale_color_manual(values = cbbPalette) +
  stat_summary(fun=mean, geom="line", 
             aes(x = date, 
                 y = t7sum))+
  theme_bw()+
  labs(x = "date",
       y = "Dust AOD")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x =element_blank(),
        axis.title.y = element_text(face= "bold"),
        legend.position = "none")
dus
```

## BIOTIC

#### TOtal Bacteria

```{r}
bact<-
bac %>%
  ggplot()+
  geom_boxplot(
    aes(x = date,
        y = log10(copies_mL),
        color = Site,
        group = interaction(Site,date)),
    position = "identity")+
  scale_color_manual(values = cbbPalette) +
stat_summary(fun=mean, geom="line", 
             aes(x = date, 
                 y = log10(copies_mL),
                 group=Site, 
                 color = Site)) +
  theme_bw()+
  labs(x = "date",
       y = "Total Bacteria (log(copies/mL))",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.x = element_blank(),
        axis.ticks.x =element_blank(),
        legend.position = "none")
bact
```

#### Chlorophyll

```{r}
chl_sum <- summarySE(env, measurevar="Chl_a", groupvars=c("Site", "date")) 

chl<-
  ggplot(chl_sum, 
       aes(x=date, 
           y=Chl_a, 
           color=Site)) + 
    geom_errorbar(data = chl_sum,
      aes(ymin=Chl_a-se, 
          ymax=Chl_a+se), 
      size = 0.5,
      width=0.3) +
    geom_line(size = 1) +
    geom_point(data = chl_sum)+
  theme_bw()+
  labs(x = "date",
       y = "Chl-a (mg/L)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
  
chl
```

#### TSS

```{r}
tss<-
  daily %>%
  ggplot() + geom_line(
  aes(
    x = date,
    y = tss,
    color = Site),
  size = 1)+
  theme_bw()+
  labs(
    x = "date",
    y = "TSS (mg/L)",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
   axis.text.x = element_blank(),
    axis.title.y = element_text(size = 13, face = "bold"),
    axis.text.y = element_text(size = 7),
    legend.key.size = unit(0.3,'cm'),
    legend.position = "none")+
    scale_color_manual(values = cbbPalette)
tss
```

#### Vibrio Copies/mL

```{r}
cop<-
  copies %>%
ggplot() + geom_boxplot(
    aes(x = date,
        y = copies_mL,
        color= Site,
        group = interaction(date, Site)),
        position = "identity") +
  theme_bw()+
  labs(x = "Date",
       y = "Total Vibrio (copies/mL)") +
  theme(axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        legend.position = "none",
        axis.title.y = element_text(face = "bold"))+
  scale_x_date(breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+


#(aes(x=as.Date('2022-07-12'),xend=as.Date('2022-07-18'),y=154323
#,yend=154323), color = "#4c848c", size = 2)+
#annotate("text", x = as.Date('2022-07-15'), y =155000, label = "***", color = "#4c848c", fontface="bold", size = 7)+

#geom_segment(aes(x=as.Date('2022-07-12'),xend=as.Date('2022-07-14'),y=90000
#,yend=90000), color = "#809C52", size = 2)+
#annotate("text", x = as.Date('2022-07-13'), y =91000, label = "***", color = "#809C52", fontface="bold", size = 7)+
  
stat_summary(fun=mean, geom="line", 
             aes(x = date, 
                 y = copies_mL,
                 group=Site, 
                 color = Site)) 
cop
ggsave(here("results", "plots", "env", "total_vib.png"))
```

#### Vc

```{r}
vc_sum1<-
  vc_sum %>%
  filter(site %in% "Blind Oso")

vc_bo<-
ggplot(vc_sum1, 
       aes(x=date, 
           y=copies_mL, 
           color=site)) + 
    geom_errorbar(data = vc_sum1[vc_sum1$point_shape == "16",],
      aes(ymin=copies_mL-se, 
          ymax=copies_mL+se), 
      width=0.3,
      size = 1) +
    geom_errorbar( data = vc_sum1[vc_sum1$point_shape == "1" ,],
      aes(ymin=0, 
          ymax=0), 
      width=0) +
    geom_line(size = 1) +
    geom_point(data = vc_sum1, shape= vc_sum1$point_shape, size = 2.5)+
  theme_bw()+
  labs(x = "Date",
       y = "V. cholerae (copies/mL)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(#axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 13, face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none")
vc_bo
```

#### Vv

```{r}
vv_sum1<-
  vv_sum %>%
  filter(site %in% "Blind Oso")

vv_bo<-
ggplot(vv_sum1, 
       aes(x=date, 
           y=copies_mL, 
           color=site)) + 
    geom_errorbar(data = vv_sum1[vv_sum1$point_shape == "16",],
      aes(ymin=copies_mL-se, 
          ymax=copies_mL+se), 
      width=0.3,
      size = 1) +
    geom_errorbar( data = vv_sum1[vv_sum1$point_shape == "1" ,],
      aes(ymin=0, 
          ymax=0, 
      width=0)) +
    geom_line(size = 1) +
    geom_point(data = vv_sum1, shape= vv_sum1$point_shape, size = 2.5)+
  theme_bw()+
  labs(x = "Date",
       y = "V. vulnificus (copies/mL)",
       color = "Site")+
  scale_x_date(date_breaks = "2 day", date_labels = "%b %d")+
  scale_color_manual(values = cbbPalette)+
  theme(#axis.text.x = element_blank(),
        axis.title.x = element_blank(),
       # axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 13, face = "bold"),
        axis.text.y = element_text(size = 10),
        legend.position = "none") 
vv_bo
```

# COMBINE

## Temp/Sal

```{r}
fig<- ggarrange(temp,
                sal+
                #nn,
                #ortho,
                #amm,
                #din,
                #don,
                #doc,
                #toc+
                #pH,
                #tss,
                #tn,
                #sil,
                #cop,
                #tdn,
               # do+
                #secchi,
                #din_dip,
                #chl+
                font("x.text", size = 8.5),
                ncol = 1, 
                nrow = 2,
                align = "v",
                common.legend  = TRUE)

fig


```

## Chl/Bact

```{r}
#CHLBAC<-
 # ggarrange(bact, chl +font("x.text", size = 8.5),
  #        nrow = 2,
   #       ncol = 1,
    #      align = "v",
     #     common.legend = TRUE)

#annotate_figure(CHLBAC,
              # bottom = text_grob("Total Bacteria is on a log-scale",
               #                   hjust = 1.2, x = 1, face = "bold", size = 7))
```

# TSS, DO

```{r}
fig<- ggarrange(#temp,
                #sal+
                #nn,
                #ortho,
                #amm,
                #din,
                #don,
                #doc,
                tss,
                #toc+
                #pH,
                #tn,
                #sil,
                #cop,
                #tdn,
                do+
                #secchi,
                #din_dip,
                #chl+
                font("x.text", size = 8.5),
                ncol = 1, 
                nrow = 2,
                align = "v",
                common.legend  = TRUE)

fig

```

# P and C

```{r, fig.width=3, fig.height=3.5}
  ggarrange(ortho, doc, toc +font("x.text", size = 8.5),
          nrow = 3,
          ncol = 1,
          align = "v",
          common.legend = TRUE)
```

# Nitrate

```{r}
NITRATE<-
  ggarrange(nn,don,amm, tdn, 
          din +font("x.text", size = 8.5),
          tn+font("x.text", size = 8.5),
          nrow = 3,
          ncol = 2,
          align = "v",
          common.legend = TRUE)

annotate_figure(NITRATE,
               bottom = text_grob("DIN = NH4+ + NO3- + NO2- ; DON = TDN - DIN",
                                  hjust = 1.2, x = 1, face = "bold", size = 7))
               
```

# Redfield

```{r}
 ggarrange(din, ortho, din_dip +font("x.text", size = 8.5),
          nrow = 3,
          ncol = 1,
          align = "v",
          common.legend = TRUE)
```

# FIGURE FOR PPT

```{r, fig.width=3, fig.height= 4}
 ggarrange(amm,chl, bact, 
          cop +font("x.text", size = 8.5),
          nrow = 4,
          ncol = 1,
          align = "v")
```

# ALL

```{r, fig.height=2, fig.width=8}
  ggarrange(amm,ortho, nn,tdn,toc,doc +font("x.text", size = 10, angle = 45),don+font("x.text", size = 10,angle = 45),din+font("x.text", size = 10,angle = 45),
            tn +font("x.text", size = 10,angle = 45, hjust = 1),
          chl+font("x.text", size = 10,hjust =1 ,angle = 45),
          nrow = 2,
          ncol = 5,
          align = "v",
          common.legend = TRUE)
```

# Make clean datatable for writing

```{r}
single<-
  ysi %>%
  dplyr::select(date, Site,
                
         Chl_a
         
         )

```

```{r}
g<-
  single %>%
  filter(Site %in% "Gulf")

c<-
  single %>%
  filter(Site %in% "Canals")

b<-
  single %>%
  filter(Site %in% "Blind Oso")
```

```{r}
mean(b$Chl_a)
mean(c$Chl_a)
mean(g$Chl_a)
```

# 
