---
title: "Environmental Parameters"
format:
  html:
    theme: default
---

*This dataset contains environmental parameters: Temp, SAL, Nutrients*

# Getting Started

#### Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
library(lubridate)
library(kableExtra) #Tables
```

#### Data

```{r}
d1<- read_csv(here("data", "processed_data", "tx_master.csv"))
```

# Cleaning

#### Daily and Monthly data frames

```{r}
daily<- d1 %>%
  filter(Type %in% "Daily")

monthly<- d1 %>% 
  mutate(Type = case_when(d1$date == "2022-07-07"  ~ "Monthly", #This makes 7-7-22 a monthly value for July
                          d1$Type == "Monthly" ~ "Monthly")) %>%
  filter(Type %in% "Monthly") 
```

# Plots

#### Temperature

```{r}
temp2<- monthly %>% ggplot() + geom_point(
  aes(
    x = date,
    y = temp,
    color = site,
    group = date),
  size = 1)+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date",
    y = "Temperature (°C)",
    title = "Monthly Temperatures",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
   # axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.text.x = element_text(hjust = 1, angle = 45),
    axis.text.y = element_text(size = 15),
    axis.title.y = element_text(size = 15),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")


temp2
  
```

#### Salinity

```{r}
sal2<- monthly %>% ggplot() + geom_point(
  aes(
    x = date,
    y = sal,
    color = site,
    group = date),
  size = 1)+
  facet_wrap(~site)+
  theme_bw()+
  labs(
    y = "Salinity",
    title = "Monthly Salinities",
    color = "Site")+
     scale_x_date(date_breaks="1 month", date_labels="%b")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.text.x = element_text(hjust = 1, angle =45),
    axis.text.y = element_text(size = 15),
   # axis.ticks.x = element_blank(),
    legend.position = "none")+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))


sal2
```

#### Total Vibrio

```{r}
fig3 <- monthly %>%
  ggplot()+geom_point(
  aes(x = date,
      y = copies_mL,
      color = site,
      group = date),
  size = 1)+
  facet_wrap(~site)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Copies/mL",
    title = "Monthly Total Vibrio") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20),  #center title
    axis.title.x = element_blank(),
    axis.text.x = element_text(hjust = 1, angle = 45),
    axis.title.y = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    legend.position = "none")+ #Removes legend
 scale_x_date(date_breaks="1 month", date_labels="%b")+

scale_color_manual(values = c("Blind Oso" = "#809C52",
                              "Canals" = "#ba4716",
                              "Gulf" = "#4c848c"))
fig3
```

##### Combine Temp and Salinity Monthly

```{r}
figp<- ggarrange(temp2,sal2, fig3 + font("x.text", size = 10), ncol = 1, nrow = 3,align = "v")

figp
```

#### Ammonium

```{r}
amm<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = amm,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
amm
```

#### Chlorophyl

```{r}
chl<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = chl,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
chl
```

#### DO (mg/L)

```{r}
do_mgl<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = do_mgl,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
do_mgl
```

#### DO (%)

```{r}
do_per<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = do_per,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
do_per
```

#### pH

```{r}
ph<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = pH,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
ph
```

#### Secchi

```{r}
secchi<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = secchi,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))

secchi
```

#### N+N

```{r}
nn<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = nn,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c")) +
  theme_bw() +
  labs(x = "Month",
       y = "N+N (µM)", 
       title = "Nitrate + Nitrite")

nn
```

#### Orthophosphate

```{r}
orthop<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = orthop,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))+
  theme_bw() +
  labs(x = "Month",
       y = "Orthophosphate (µM)",
       title = "Orthophosphate")
orthop
```

#### Silicate

```{r}
sil<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = sil,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))

sil
```

#### DIN

```{r}
din<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = din,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
din
```

#### DIN:DIP

```{r}
din_dip<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = din_dip,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))

din_dip
```

#### TDN

```{r}
tdn<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = tdn,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))

tdn
```

#### DON

```{r}
don<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = don,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
don
```

#### DOC

```{r}
doc<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = doc,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
doc
```

#### TOC

```{r}
toc<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = toc,
    color = site))+
  scale_x_date(date_breaks = "1 month", date_labels = "%b")+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
toc
```

#### TN

```{r}
tn<- monthly %>%
  ggplot() + geom_line(
    aes(
      x = date,
      y = tn,
    color = site))+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "#4c848c"))
tn
```

# Monthly Averages

We are taking out 5/20 and 5/24 here.

#### Make New Site-specific Data sets

<!--# This master dataset has multiple tim points. I need to just get averages from envirionmental data with one entry per date -->

```{r}
avg<- 
  monthly %>%
  filter(!date == as.Date('2022-05-24') & !date == as.Date('2022-05-20'),#Gets ride of extra dates in May
         hr_cst %in% "01") 

b_avg<-
  avg %>%
  filter(site %in% "Blind Oso") 
b_avg<- 
  b_avg %>%
  rbind(b_avg, sapply(b_avg, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else "")) %>% #Adds a new row with average
  select(6,9:26) #Select columns of interest


c_avg<-
  avg %>%
  filter(site %in% "Canals")
c_avg<-
  c_avg %>%
  rbind(c_avg, sapply(c_avg, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else "")) %>%
  select(6,9:26)

r_avg<-
  avg %>%
  filter(site %in% "Gulf")
r_avg<-
  r_avg %>%
  rbind(r_avg, sapply(r_avg, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else "")) %>%
  select(6,9:26)
```

#### Extract Average Values

```{r}
b_nn<- b_avg$nn[89] 
b_orthop<- b_avg$orthop[89]

c_nn<- c_avg$nn[89]
c_orthop<- c_avg$orthop[89]

r_nn<- r_avg$nn[89]
r_orthop<- r_avg$orthop[89]

#DF
average_df<- 
  tibble(Site  = c("Blind Oso", "Canals", "Gulf"),
             NN = c(b_nn, c_nn, r_nn),
             OrthoP = c(b_orthop, c_orthop, r_orthop))
kable(average_df)
```

#### 
