---
title: "Stepwise Regression"
format:
  html:
    theme: default
---

# Intro

[LINK](https://www.statology.org/stepwise-regression-r/)

#### Libraries

```{r, inlclude = FALSE}
library(tidyverse)
library(here)
```

#### Data

```{r}
master<- read.csv(here("data", "processed_data", "tx_master.csv"))
b<- read.csv(here("data", "processed_data", "bo_master_daily.csv"))
c<- read.csv(here("data", "processed_data", "c2_master_daily.csv"))
r<- read.csv(here("data", "processed_data", "rd_master_daily.csv"))
```

# Cleaning

#### Select Columns

<!--# Can come back through here to change what we want to keep (species, or VAI) -->

```{r}
b<-
  b %>%
  select(!c(X, dust, cfu_yel, cfu_gre, hf_copies_mL, Vc, Vv, Vp, tot_bacteria, tss, VAI, cfu_tot, date))

c<-
  c %>%
  select(!c(X, dust, cfu_yel, cfu_gre, hf_copies_mL, Vc, Vv, Vp, tot_bacteria, tss, VAI, cfu_tot, date))

r<-
  r %>%
  select(!c(X, dust, cfu_yel, cfu_gre, hf_copies_mL, Vc, Vv, Vp, tot_bacteria, tss, VAI, cfu_tot, date))
```

# Stepwise Regression

Response variable is **copies_mL (Total Vibrio)** and predictor variables are all else.

## 1. Forward Stepwise Regression

### BLIND OSO

```{r}
#Define Intercept-only (null) Model
intercept_only <- lm(copies_mL ~ 1, data=b)

#Define Model with All Predictors
all <- lm(copies_mL ~ ., data=b)

#Perform FSR
forward <- step(intercept_only, direction='forward', scope=formula(all), trace=0)
```

**Note**: The argument trace=0 tells R not to display the full results of the stepwise selection. This can take up quite a bit of space if there are a large number of predictor variables.

#### View Results of FSR

```{r}
forward$anova
```

-   First, we fit the intercept-only model. This model had an AIC of **239.8795**

-   Next, we fit every possible one-predictor model. The model that produced the lowest AIC and also had a statistically significant reduction in AIC compared to the intercept-only model used the predictor *dust_lag*. This model had an AIC of **235.19**.

-   Next, we fit every possible two-predictor model. The model that produced the lowest AIC and also had a statistically significant reduction in AIC compared to the single-predictor model added the predictor *do_per.* This model had an AIC of **229**.

-   Next, we fit every possible three-predictor model. The model that produced the lowest AIC and also had a statistically significant reduction in AIC compared to the two-predictor model added the predictor *temp*. This model had an AIC of **225.52**.

-   Next, we fit every possible four-predictor model. This keeps going until none of these models produced a significant reduction in AIC, thus we stopped the procedure.

#### View Final Model

```{r}
b_model<- forward$coefficients
b_model
```

The final model turns out to be:

**copies_mL \~ 854100.56 + 88753\*dust_lag - 1364\*do_per - 24819\*temp + 26386\*amm +25\*doc - 1101\*din_dip**

### CANALS

```{r}
#Define Intercept-only (null) Model
intercept_only <- lm(copies_mL ~ 1, data=c)

#Define Model with All Predictors
all <- lm(copies_mL ~ ., data=c)

#Perform FSR
forward <- step(intercept_only, direction='forward', scope=formula(all), trace=0)

#View Results of FSR
forward$anova

#View Final Model
c_model<- forward$coefficients
c_model
```

### GULF

```{r}
#Define Intercept-only (null) Model
intercept_only <- lm(copies_mL ~ 1, data=r)

#Define Model with All Predictors
all <- lm(copies_mL ~ ., data=r)

#Perform FSR
forward <- step(intercept_only, direction='forward', scope=formula(all), trace=0)

#View Results of FSR
forward$anova

#View Final Model
r_model<- forward$coefficients
r_model
```

<!--# Should also check out Regularization Section in MADA Module 10 -->

## 2. Backwards Stepwise Regression

### BLIND OSO

```{r}

```

### CANALS

```{r}
#define intercept-only model
intercept_only <- lm(copies_mL ~ 1, data=c)

#define model with all predictors
all <- lm(copies_mL ~ ., data=c)

#perform backward stepwise regression
backward <- step(all, direction='backward', scope=formula(all), trace=0)

#view results of backward stepwise regression
backward$anova

#view final model
backward$coefficients
```

### GULF

```{r}

```
