---
title: "Untitled"
format:
  html:
    theme: default
---

[LINK](https://www.r-bloggers.com/2021/08/how-to-perform-tukey-hsd-test-in-r/)

#### Libraries

```{r, include=FALSE}
library(here)
library(tidyverse)
library(multcomp)
select<- dplyr::select
```

#### Data

Note: This data is pridced in total_copies_calculator code. I kept qPCR triplicates (i.e. did not average) for this

<!--# Actually we dont need these -->

```{r, include = FALSE}
#vib<- read_csv(here::here("data", "processed_data", "ANOVA Data", "total_vibrio"))
#bac<- read_csv(here::here("data", "processed_data", "ANOVA Data", "total_bacteria.csv"))
#hf<- read_csv(here::here("data", "processed_data",  "ANOVA Data", "hf183.csv"))
#cfu<- read_csv(here::here("data", "processed_data",  "ANOVA Data", "cfu_anova.csv"))
#vc<- read_csv(here::here("data", "processed_data",  "ANOVA Data", "vc_anova.csv"))
#vv<- read_csv(here::here("data", "processed_data",  "ANOVA Data", "vv_anova.csv"))
```

```{r}
data<- read_csv(here('data', 'processed_data', 'tx_master.csv'))
dust<- read_csv(here('data', 'processed_data', 'dust', 'dust_master.csv'))
```

# Clean

```{r}
t<- 
  data %>%
  select(copies_mL, Va, Vv, Vc, Vp, tot_bacteria, hf_copies_mL, date, site, hr_cst, cfu_tot) %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19')),
         hr_cst %in% "01") %>%
  filter(!date %in% as.Date('2022-07-10')) 
```

#### Total Vibrio

**We are going to split the timeseries into low dust (7-12) and high dust days (13-19) and then take the average**

```{r}
vib<-
  t %>%
  select(date,copies_mL, site) %>%
  mutate(date = substr(date, 9,10)) %>%  #Date needs to not be as.Date format
  mutate(dust = case_when(date <=12 ~ "low",
                          date >12 ~ "high"))
b<-
  vib %>%
  filter(site %in% "Blind Oso") %>%
  select(copies_mL, dust)  
c<-
  vib %>%
  filter(site %in% "Canals") %>%
  dplyr::select(copies_mL, dust)

r<-
  vib %>%
  filter(site %in% "Gulf") %>%
  dplyr::select(copies_mL, dust)
```

#### CFU

```{r}
cfu<-
  t %>%
  select(date, cfu_tot,site) %>%
  mutate(dust = case_when(date <= as.Date('2022-07-12') ~ "low",
                          date > as.Date('2022-07-12') ~ "high")) %>%
  dplyr::select(date, site, cfu_tot, dust)

b_cfu<-
  cfu %>%
  filter(site %in% "Blind Oso") %>%
  dplyr::select(!site)
c_cfu<-
  cfu %>%
  filter(site %in% "Canals") %>%
  dplyr::select(!site)
r_cfu<-
  cfu %>%
  filter(site %in% "Gulf") %>%
  dplyr::select(!site)
```

#### Species

```{r}
vc<-
  t %>%
  select(date, Vc,site) %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) %>%
  mutate(dust = case_when(date <= as.Date('2022-07-12') ~ "low",
                          date > as.Date('2022-07-12') ~ "high")) 
vv<-
  t %>%
  select(date, Vv,site) %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) %>%
  mutate(dust = case_when(date <= as.Date('2022-07-12') ~ "low",
                          date > as.Date('2022-07-12') ~ "high")) 
 

b_vc<-
  vc %>%
  filter(site %in% "Blind Oso") %>%
  dplyr::select(Vc, dust)
b_vv<-
  vv %>%
  filter(site %in% "Blind Oso") %>%
  dplyr::select(Vv, dust)

r_vc<-
  vc %>%
  filter(site %in% "Gulf") %>%
  dplyr::select(Vc, dust)

```

#### Dust

```{r}
dust<-
  dust %>%
  select(date, t7sum) %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19')))%>%
  mutate(event = case_when(date <= as.Date('2022-07-12') ~ "low",
                          date > as.Date('2022-07-12') ~ "high"))
```

# T.test

#### Dust

```{r}
t.test(t7sum ~ event, data = dust)
```

#### Total Vibrio

```{r}
#BO
t.test(copies_mL ~ dust, data = b)

#C2
t.test(copies_mL ~ dust, data = c)

#RD
t.test(copies_mL ~ dust, data = r)
```

#### CFU

```{r}
#BO
t.test(cfu_tot ~ dust, data = b_cfu)

#C2
t.test(cfu_tot ~ dust, data = c_cfu)

#RD
t.test(cfu_tot ~ dust, data = r_cfu)
```

#### Species

```{r}
#BO Vv
t.test(Vv ~ dust, data = b_vv)

#BO Vc
t.test(Vc ~ dust, data = b_vc)

#RD Vc
t.test(Vc ~ dust, data = r_vc)
```

# Find X Fold increases

**Averages of high and lo dust days taken and (F-I)/I**

#### Total Vibrio

```{r}
b_fold<-
  b %>%
  group_by(dust) %>%
  summarise_at(vars(copies_mL), list(name = mean))
  ((b_fold[1,2]  - b_fold[2,2] ) / b_fold[2,2])*100

r_fold<-
  r %>%
  group_by(dust) %>%
  summarise_at(vars(copies_mL), list(name = mean))
  ((r_fold[1,2]  - r_fold[2,2] ) / r_fold[2,2])*100

```

#### CFU

```{r}
b_fold<-
  b_cfu %>%
  group_by(dust) %>%
  summarise_at(vars(cfu_tot), list(name = mean))
  ((b_fold[1,2]  - b_fold[2,2] ) / b_fold[2,2])*100

r_fold<-
  r_cfu %>%
  group_by(dust) %>%
  summarise_at(vars(cfu_tot), list(name = mean))
  ((r_fold[1,2]  - r_fold[2,2] ) / r_fold[2,2])*100
```

#### Species

```{r}
b_vc_fold<- 
  b_vc %>%
  group_by(dust) %>%
  summarise_at(vars(copies_mL), list(name = mean))
  ((b_vc_fold[1,2]  - b_vc_fold[2,2] ) / b_vc_fold[2,2])*100

b_vv_fold<- 
  b_vv %>%
  group_by(dust) %>%
  summarise_at(vars(copies_mL), list(name = mean))
  ((b_vv_fold[1,2]  - b_vv_fold[2,2] ) / b_vv_fold[2,2])*100

r_vc_fold<- 
  r_vc %>%
  group_by(dust) %>%
  summarise_at(vars(copies_mL), list(name = mean))
  ((r_vc_fold[1,2]  - r_vc_fold[2,2] ) / r_vc_fold[2,2])*100
```
