---
title: "vp daily"
format:
  html:
    theme: default
---

# LIBS/DATA

#### LIBRARIES

```{r}
library(here)
library(tidyverse)
library(lubridate)
library(ggpubr) #Stacking Plots
```

#### DATA

```{r, include=FALSE}
master<- read_csv(here("data", "processed_data","tx_master.csv"))
```

# Clean

```{r}
master<-
  master %>%
  rename("Site" = "site")
```

# DAILY PLOTS

## Vp

```{r}
#png(file = here("results", "plots", "species_specific", "vp_daily.png"))
 vp<-
   master %>%
   filter(Type %in% "Daily") %>%
  ggplot() + geom_line(
    aes(x = date,
        y = Vp,
        color = Site))+ 
  #facet_wrap(~site)  +
  labs(x = "Date",
       y = "V. parahaemolyticus")+
      # title = "Daily Vibrio parahaemolyticus",
       #caption = "BO was 1:10")+
  theme_bw()+
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(hjust = 1, angle = 45),
    legend.position = "none")+
  scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))
# dev.off()

 ggsave(here("results", "plots", "qpcr", "vp_daily.png"))
```

## Vv

```{r}
#png(file = here("results", "plots", "species_specific", "vv_daily.png"))
vv<-
 master %>%
   filter(Type %in% "Daily") %>%
  ggplot() + geom_line(
    aes(x = date,
        y = Vv,
        color = Site))+ 
 # facet_wrap(~site)  +
  labs(x = "Date",
       y = "V. vulnificus")+
     #  title = "Daily Vibrio vulnificus")+
  theme_bw()+
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(hjust = 1, angle = 45),
    legend.position = "none")+ 
  scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))
#dev.off()

 ggsave(here("results", "plots","qpcr", "vv_daily.png"))
```

## Vc

For Vc, we ran it initial with all three sites. Then tested BO for INH, and it looked inhibited. So we ran 1:50 (still inh), 1:100 (too dilute), and 1:50 one more time. For the 1:50 trials we had a total of 5 reps (which is what we see below for BO). We have the data (raw/processed) for the other trials, but they have been removed here so as to clear up space.

```{r}
vc<-
  master %>%
   filter(Type %in% "Daily") %>%
  ggplot() + geom_line(
    aes(x = date,
        y = Vc,
        color = Site))+ 
  #facet_wrap(~site)  +
  labs(x = "",
       y = "V. cholerae",
       color = "Site")+
      # title = "Daily Vibrio cholerae ",
      # caption = "Blind Oso was 1:50")+
  theme_bw()+
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = c(0.3,0.6))+ 
  scale_color_manual(values = c("Blind Oso" = "#809C52", #5 replicates
                                "Canals" = "#ba4716",#3
                                "Gulf" = "4c848c"))#3

 ggsave(here("results", "plots", "qpcr","vc_daily.png"))
```

#### 

## Va

```{r}
va<-
  master %>%
   filter(Type %in% "Daily") %>%
  ggplot() + geom_line(
    aes(x = date,
        y = Va,
        color = Site))+ 
 # facet_wrap(~site)  +
  labs(x = "",
       y = "V. alginolyticus")+
       #title = "Daily Vibrio alginolyticus ")+
  theme_bw()+
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "none")+ 
  scale_color_manual(values = c("Blind Oso" = "#809C52", #5 replicates
                                "Canals" = "#ba4716",#3
                                "Gulf" = "4c848c"))#3

 ggsave(here("results", "plots", "qpcr","va_daily.png"))
```

#### Combine

```{r}
ggarrange(va,vc,vp,vv,
          ncol = 2,nrow =2,
          common.legend = TRUE,
          align = "hv")

ggsave(here('results', 'plots', 'qpcr', 'species_by_site.png'))
```

#### Clean DF for writing

```{r}
yeet<-
  master %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19')),
         hr_cst %in% "01",
         !date %in% as.Date('2022-07-10')) %>%
  dplyr::select(Site, date, 
         Vc)
```

## All Species

<!--# Make new df to have species legend -->

```{r}
spp<-
  master %>%
  filter(hr_cst %in% "01",
         date %in% as.Date('2022-07-07') : as.Date('2022-07-19'))%>%
  select(date, Va, Vc, Vp, Vv, site)

va<-
  spp %>%
  select(site, date, Va) %>%
  mutate(species = "Va") %>% 
  rename("copies_mL" = "Va")

vc<-
  spp %>%
  select(site, date, Vc) %>%
  mutate(species = "Vc") %>% 
  rename("copies_mL" = "Vc")

vp<-
  spp %>%
  select(site, date, Vp) %>%
  mutate(species = "Vp") %>% 
  rename("copies_mL" = "Vp")

vv<-
  spp %>%
  select(site, date, Vv) %>%
  mutate(species = "Vv") %>% 
  rename("copies_mL" = "Vv")

spp<-
  rbind(va,vc,vv,vp)
```

#### Blind Oso Species

```{r}
bo_spp<-
  spp %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = species)) +
  theme_bw() +
  labs(x = "Date",
       y = "Gene Copies per mL",
       title = "Blind Oso",
       color = "Species") +
  theme(legend.position = c(0.25, 0.8),
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"),
        axis.text.x = element_text(hjust = 1, angle = 45))
bo_spp
  
ggsave(here("results", "plots", "qpcr","bo_all_daily.png"))
```

#### Canals

```{r}
c2_spp<-
  spp %>%
  filter(site %in% "Canals") %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = species)) +
  theme_bw() +
  labs(x = "Date",
       y = "Gene Copies per mL",
       title = "Canals",
       color = "Species") +
  theme(legend.position = "none",
         axis.text.x = element_text(hjust = 1, angle = 45))
c2_spp
  
ggsave(here("results", "plots", "qpcr","c2_all_daily.png"))
```

#### Gulf

```{r}
rd_spp<-
  spp %>%
  filter(site %in% "Gulf") %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = species))+
  theme_bw() +
  labs(x = "Date",
       y = "Gene Copies per mL",
       title = "Gulf",
       color = "Species") +
  theme(legend.position = "none",
         axis.text.x = element_text(hjust = 1, angle = 45))
rd_spp
  
ggsave(here("results", "plots", "qpcr","rd_all_daily.png"))
```

## Combine

```{r}
all_spp<-
  ggarrange(bo_spp, c2_spp, rd_spp,
            nrow = 1,
            ncol = 3)
all_spp

ggsave(here("results", "plots", "qpcr","species_all_daily.png"))
```

#### Clean DF For Writing

```{r}
clean<-
  spp %>%
  filter(site %in% "Gulf" &
         species %in% "Vc")
```

```{r}
clean<-
  clean %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-13')))

mean(clean$copies_mL)
```

# MONTHLY PLOTS

#### Vp

```{r}
#png(file = here("results", "plots", "species_specific", "vp_mon.png"))

  master %>%
  filter(Type %in% "Monthly") %>%
  ggplot() +
    geom_line(
    aes(
      x = date,
      y = Vp,
      color = site),
    size = 1)+ 
  theme_bw()+
     labs(title = "Vp",
       x = "Date",
       y = "Vibrio gene copies/mL") +
    facet_wrap(~site) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") +
  scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
  scale_x_date(date_breaks = "1 month", date_labels = "%b")

#dev.off()

 ggsave(here("results", "plots", "qpcr","vp_monthly.png"))
```

#### Vv

```{r}
#png(file = here("results", "plots", "species_specific", "vv_mon.png"))
  master %>%
  filter(Type %in% "Monthly") %>%
  ggplot() +
    geom_line(
    aes(
      x = date,
      y = Vv,
      color = site),
    size = 1)+ 
  theme_bw()+
     labs(title = "Vv",
       x = "Date",
       y = "Vibrio gene copies/mL") +
    facet_wrap(~site) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") +
  scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
  scale_x_date(date_breaks = "1 month", date_labels = "%b")
#dev.off()

  ggsave(here("results", "plots", "qpcr","vv_monthly.png"))
```

#### Va

```{r}
  master %>%
  filter(Type %in% "Monthly") %>%
  ggplot() +
    geom_line(
    aes(
      x = date,
      y = Va,
      color = site),
    size = 1)+ 
  theme_bw()+
     labs(title = "Va",
       x = "Date",
       y = "Vibrio gene copies/mL") +
    facet_wrap(~site) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") +
  scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
  scale_x_date(date_breaks = "1 month", date_labels = "%b")
#dev.off()

 ggsave(here("results", "plots","qpcr", "va_monthly.png"))
```

#### Vc

```{r}
  master %>%
  filter(Type %in% "Monthly") %>%
  ggplot() +
    geom_line(
    aes(
      x = date,
      y = Vc,
      color = site),
    size = 1)+ 
  theme_bw()+
     labs(title = "Vc",
       x = "Date",
       y = "Vibrio gene copies/mL") +
    facet_wrap(~site) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") +
  scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
  scale_x_date(date_breaks = "1 month", date_labels = "%b")
#dev.off()

 ggsave(here("results", "plots","qpcr", "vc_monthly.png"))
 
```

#### Plot

##### Blind Oso

```{r}
bo_spp_monthly<-
  master %>%
  filter(Type %in% "Monthly",
         site %in% "Blind Oso") %>%
  ggplot() +
  geom_line(
    aes(
      x = date,
      y = Vc),
      color = "#00BFC4",
    size = 1)+ 
  geom_line(
    aes(
      x = date,
      y = Vv),
      color = "#00BA38",
    size = 1)+ 
    geom_line(
    aes(
      x = date,
      y = Vp),
      color = "#C77CFF",
    size = 1)+ 
  theme_bw()+
     labs(title = "Vibrio Species at Blind Oso",
       x = "Date",
       y = "Vibrio gene copies/mL") +
  theme(axis.text.x = element_text(hjust = 1, angle = 45),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") 

bo_spp_monthly

#dev.off()
 ggsave(here("results", "plots","qpcr", "bo_all_monthly.png"))
```

##### Canals

```{r}
c2_spp_monthly<-
  master %>%
  filter(Type %in% "Monthly",
         site %in% "Canals") %>%
  ggplot() +
  geom_line(
    aes(
      x = date,
      y = Vc),
      color = "#00BFC4",
    size = 1)+ 
  geom_line(
    aes(
      x = date,
      y = Vv),
      color = "#00BA38",
    size = 1)+ 
    geom_line(
    aes(
      x = date,
      y = Vp),
      color = "#C77CFF",
    size = 1)+ 
  theme_bw()+
     labs(title = "Vibrio Species at Canals",
       x = "Date",
       y = "Vibrio gene copies/mL") +
  theme(axis.text.x = element_text(hjust = 1, angle = 45),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") 

c2_spp_monthly

#dev.off()
 ggsave(here("results", "plots","qpcr", "c2_all_monthly.png"))
```

##### Gulf

```{r}
rd_spp_monthly<- 
  master %>%
  filter(Type %in% "Monthly",
         site %in% "Gulf") %>%
  ggplot() +
  geom_line(
    aes(
      x = date,
      y = Vc),
      color = "#00BFC4",
    size = 1)+ 
  geom_line(
    aes(
      x = date,
      y = Vv),
      color = "#00BA38",
    size = 1)+ 
    geom_line(
    aes(
      x = date,
      y = Vp),
      color = "#C77CFF",
    size = 1)+ 
  theme_bw()+
     labs(title = "Vibrio Species at Gulf",
       x = "Date",
       y = "Vibrio gene copies/mL") +
  theme(axis.text.x = element_text(hjust = 1, angle = 45),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") 

rd_spp_monthly

#dev.off()
 ggsave(here("results", "plots", "qpcr","rd_all_monthly.png"))
```
