---
title: "COm"
format:
  html:
    theme: default
---

# Getting Started

#### Libraries

```{r}
library(tidyverse)
library(here)
library(ggpubr)
library(lubridate)
library(kableExtra) #Tables
```

#### Data

```{r, include = FALSE}
d1<- read_csv(here("data", "processed_data", "tx_master.csv"))
sp<- read_rds(here("data", "processed_data", "qpcr","species_copies_monthly.rds"))
sp_d<- read_rds(here("data", "processed_data", "qpcr","species_copies.rds"))
dust_sum<-read_csv(here("data", "processed_data", "dust", "dust_master.csv")) #Dust

```

# Cleaning

#### Daily and Monthly data frames

```{r}
daily<- d1 %>%
  filter(Type %in% "Daily")

monthly<- d1 %>% 
  mutate(Type = case_when(d1$date == "2022-07-07"  ~ "Monthly", #This makes 7-7-22 a monthly value for July
                          d1$Type == "Monthly" ~ "Monthly")) %>%
  filter(Type %in% "Monthly") 
```

#### Dust

```{r}
daily_dust_sum<- dust_sum %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) 
```

# Plots

## MONTHLY

### Total Vibrio

#### Blind Oso

```{r}
tot_bo <- monthly %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Vibrio gene copies/mL",
    title = "Blind Oso: Total Vibrio Concentrations",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    #axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

tot_bo
```

#### Canals

```{r}
tot_c2 <- monthly %>%
  filter(site %in% "Canals") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Vibrio gene copies/mL",
    title = "Canals: Total Vibrio Concentrations",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
   # axis.ticks.x = element_blank(),
   # axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

tot_c2
```

#### All on one plot

```{r}
tot_all <- monthly %>%
  #filter(site %in% "Canals") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Vibrio gene copies/mL",
    title = "Monthly Total Vibrio Concentrations",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
   # axis.ticks.x = element_blank(),
   # axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = c(0.1,0.8),
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

tot_all
```

#### Gulf

```{r}
tot_rd <- monthly %>%
  filter(site %in% "Gulf") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Vibrio gene copies/mL",
    title = "Gulf: Total Vibrio Concentrations",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
   # axis.ticks.x = element_blank(),
   # axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

tot_rd
```

### Species

#### Blind Oso

```{r}
bo_spp_monthly<- sp%>%
  filter(site %in% "Blind Oso",
         !type %in% "V. alginolyticus") %>% #Take out Va for now
  ggplot() + 
  geom_point(
    aes(
      x = date,
      y = copies_mL,
      color = type),
    size = 2)+
  geom_line(
    aes(
      x = date,
      y = copies_mL,
      color = type),
    size = 1)+ 
  theme_bw()+
     labs(title = "Vibrio Species Concentrations at Blind Oso",
       x = "Date",
       y = "Vibrio gene copies/mL",
       color = "Vibrio spp.") +
  theme(axis.text.x = element_text(hjust = 1),
        axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15),
        axis.title.y = element_text(size = 10, face = "bold"),
        legend.position = "none") + 
  scale_x_date(date_breaks="1 month", date_labels="%b")+
scale_color_manual(values = c("V. alginolyticus" = "#F8766D",
                              "V. cholerae" = "#00BFC4",
                              "V. parahaemolyticus" = "#C77CFF",
                              "V. vulnificus" = "#00BA38"))

bo_spp_monthly
```

#### Canals

```{r}
c2_spp_monthly<- sp%>%
  filter(site %in% "Canals",
         !type %in% "V. alginolyticus") %>% #Take out Va for now
  ggplot() + 
  geom_point(
    aes(
      x = date,
      y = copies_mL,
      color = type),
    size = 2)+
  geom_line(
    aes(
      x = date,
      y = copies_mL,
      color = type),
    size = 1)+ 
  theme_bw()+
     labs(title = "Vibrio Species Concentrations at the Canals",
       x = "Date",
       y = "Vibrio gene copies/mL",
       color = "Vibrio spp.") +
  theme(axis.text.x = element_text(hjust = 1),
        axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15),
        axis.title.y = element_text(size = 10, face = "bold"),
        legend.position = "none") + 
  scale_x_date(date_breaks="1 month", date_labels="%b")+
scale_color_manual(values = c("V. alginolyticus" = "#F8766D",
                              "V. cholerae" = "#00BFC4",
                              "V. parahaemolyticus" = "#C77CFF",
                              "V. vulnificus" = "#00BA38"))
c2_spp_monthly
```

#### Gulf

```{r}
rd_spp_monthly<- sp%>%
  filter(site %in% "Gulf",
         !type %in% "V. alginolyticus") %>% #Take out Va for now
  ggplot() + 
  geom_point(
    aes(
      x = date,
      y = copies_mL,
      color = type),
    size = 2)+
  geom_line(
    aes(
      x = date,
      y = copies_mL,
      color = type),
    size = 1)+ 
  theme_bw()+
     labs(title = "Vibrio Species Concentrations at the Gulf",
       x = "Date",
       y = "Vibrio gene copies/mL",
       color = "Vibrio spp.") +
  theme(axis.text.x = element_text(hjust = 1),
        axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15),
        axis.title.y = element_text(size = 10, face = "bold"),
        legend.position = "none") + 
  scale_x_date(date_breaks="1 month", date_labels="%b")+
scale_color_manual(values = c("V. alginolyticus" = "#F8766D",
                              "V. cholerae" = "#00BFC4",
                              "V. parahaemolyticus" = "#C77CFF",
                              "V. vulnificus" = "#00BA38"))
rd_spp_monthly
```

### N+N

#### Gulf

```{r}
nn_rd <- monthly %>%
  filter(site %in% "Gulf") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = nn,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = nn,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "N+N (µM)",
    title = "Gulf: Nitrate+Nitrite",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

nn_rd
```

### Ammonium

#### Blind Oso

```{r}
amm_bo <- monthly %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Ammonium (µM)",
    title = "Blind Oso: Ammonium",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

amm_bo
```

#### Canals

```{r}
amm_c2 <- monthly %>%
  filter(site %in% "Canals") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Ammonium (µM)",
    title = "Canals: Ammonium",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

amm_c2
```

#### Gulf

```{r}
amm_rd <- monthly %>%
  filter(site %in% "Gulf") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Ammonium (µM)",
    title = "Gulf: Ammonium",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

amm_rd
```

### Silicate

#### Canals

```{r}
sil_c2 <- monthly %>%
  filter(site %in% "Canals") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = sil,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = sil,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Silicate (µM)",
    title = "Canals: Silicate",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

sil_c2
```

#### Gulf

```{r}
sil_rd <- monthly %>%
  filter(site %in% "Gulf") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = sil,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = sil,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Silicate (µM)",
    title = "Gulf: Silicate",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
   # axis.ticks.x = element_blank(),
   # axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")

sil_rd
```

### OrthoP

#### Canals

```{r}
orthop_c2 <- monthly %>%
  filter(site %in% "Canals") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = orthop,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = orthop,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Orthophsphate (µM)",
    title = "Canals: Orthophosphate",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
orthop_c2
```

### DIN

#### Canals

```{r}
din_c2 <- monthly %>%
  filter(site %in% "Canals") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = din,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = din,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "DIN (µM)",
    title = "Canals: DIN",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
din_c2
```

#### Gulf

```{r}
din_rd <- monthly %>%
  filter(site %in% "Gulf") %>%
  ggplot() + 
  geom_point(
  aes(
    x = date,
    y = din,
    color = site),
  size = 2)+
  geom_line(
  aes(
    x = date,
    y = din,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "DIN (µM)",
    title = "Gulf: DIN",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))+
   scale_x_date(date_breaks="1 month", date_labels="%b")
din_rd
```

### Stack

#### BO: Amm x Tot

```{r}
ggarrange(amm_bo, tot_bo,
          nrow = 2, ncol = 1)
```

#### BO: Amm x Spp

```{r}
ggarrange(amm_bo, bo_spp_monthly,
          nrow = 2, ncol = 1)
```

#### C2: Sil x Tot

```{r}
ggarrange(sil_c2, tot_c2,
          nrow = 2, ncol = 1)
```

#### C2: DIN x Amm x OrthoP x Species

```{r, fig.height= 6.5, fig.width=5}
ggarrange(din_c2, amm_c2, orthop_c2, c2_spp_monthly, 
          nrow = 4 , ncol = 1)
```

#### RD: NN x Amm x DIN x Spp

```{r, fig.height=3, fig.width=6}
ggarrange(din_rd, amm_rd, nn_rd, sil_rd,rd_spp_monthly,
          nrow = 3 , ncol = 2)
```

#### Total All sites

```{r, fig.height=3, fig.width=3}

ggarrange(tot_bo, tot_c2, tot_rd,
          nrow = 3 , ncol = 1)
```

## DAILY

## Dust

```{r}
dust<- 
  daily_dust_sum %>% 
  ggplot() +
geom_line(
  aes(x = date,
      y = t7sum),
  color = "#935d2e",
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Dust (AOD)",
    title = "Dust AOD")+
  theme(
    plot.title = element_text(hjust = 0.5, size = 15),
    axis.title.y = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank())
  

dust
```

## Blind Oso

#### Total

```{r}
tot_bo <- daily %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Vibrio gene copies/mL",
    title = "Blind Oso: Total Vibrio Concentrations",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

tot_bo
```

#### Species

```{r}
bo_spp_daily<- sp_d%>%
  filter(site %in% "Blind Oso",
         !type %in% "V. alginolyticus") %>% #Take out Va for now
  ggplot() + 
  geom_line(
    aes(
      x = date,
      y = copies_mL,
      color = type),
    size = 1)+ 
  theme_bw()+
     labs(title = "Vibrio Species Concentrations at Blind Oso",
       x = "Date",
       y = "Vibrio gene copies/mL",
       color = "Vibrio spp.") +
  theme(axis.text.x = element_text(hjust = 1),
        axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15),
        axis.title.y = element_text(size = 10, face = "bold"),
        legend.position = "none") + 
scale_color_manual(values = c("V. alginolyticus" = "#F8766D",
                              "V. cholerae" = "#00BFC4",
                              "V. parahaemolyticus" = "#C77CFF",
                              "V. vulnificus" = "#00BA38"))

bo_spp_daily
```

#### TDN

```{r}
tdn_bo <- daily %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = tdn,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "TDN (µM)",
    title = "Blind Oso: TDN",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none") +
    #legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

tdn_bo
```

#### DIN

```{r}
din_bo <- daily %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() +
  geom_line(
  aes(
    x = date,
    y = din,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "DIN (µM)",
    title = "Blind Oso: DIN",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

din_bo
```

#### Amm

```{r}
amm_bo <- daily %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() +
  geom_line(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Ammonium (µM)",
    title = "Blind Oso: Ammonium",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
   # axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

amm_bo
```

#### Temperature

```{r}
temp_bo <- daily %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = temp,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Temperature (°C)",
    title = "Blind Oso: Temperature",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))
temp_bo
```

#### Salinity

```{r}
sal_bo <- daily %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = sal,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Salinity",
    title = "Blind Oso: Salinity",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))
sal_bo
```

#### NN

```{r}
nn_bo <- daily %>%
  filter(site %in% "Blind Oso") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = nn,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "N+N (µM)",
    title = "Blind Oso: Nitrate+Nitrite",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

nn_bo
```

## Canals

#### Total

```{r}
tot_c2 <- daily %>%
  filter(site %in% "Canals") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Vibrio gene copies/mL",
    title = "Canals: Total Vibrio Concentrations",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

tot_c2
```

## Gulf

#### Total

```{r}
tot_rd <- daily %>%
  filter(site %in% "Gulf") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = copies_mL,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Vibrio gene copies/mL",
    title = "Gulf: Total Vibrio Concentrations",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

tot_rd
```

#### Species

```{r}
rd_spp_daily<- sp_d %>%
  filter(site %in% "Gulf",
         !type %in% "V. alginolyticus") %>% #Take out Va for now
  ggplot() + 
  geom_line(
    aes(
      x = date,
      y = copies_mL,
      color = type),
    size = 1)+ 
  theme_bw()+
     labs(title = "Vibrio Species Concentrations at the Gulf",
       x = "Date",
       y = "Vibrio gene copies/mL",
       color = "Vibrio spp.") +
  theme(axis.text.x = element_text(hjust = 1),
        axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15),
        axis.title.y = element_text(size = 10, face = "bold"),
        legend.position = "none") + 
scale_color_manual(values = c("V. alginolyticus" = "#F8766D",
                              "V. cholerae" = "#00BFC4",
                              "V. parahaemolyticus" = "#C77CFF",
                              "V. vulnificus" = "#00BA38"))
rd_spp_daily
```

#### DIN

```{r}
din_rd <- daily %>%
  filter(site %in% "Gulf") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = din,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "DIN (µM)",
    title = "Gulf: DIN",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

din_rd
```

#### Amm

```{r}
amm_rd <- daily %>%
  filter(site %in% "Gulf") %>%
  ggplot() + 
  geom_line(
  aes(
    x = date,
    y = amm,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Ammonium (µM)",
    title = "Gulf: Ammonium",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 15),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 7),
    axis.title.y = element_text(size = 10, face = "bold"),
    legend.position = "none",
    legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) + #Moves legend onto plot 
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

amm_rd
```

## Stack

#### BO: DIN x Amm X TDN X NN X Spp

```{r, fig.height=3, fig.width=5}
ggarrange(temp_bo, sal_bo, tdn_bo, din_bo, nn_bo, dust, amm_bo,bo_spp_daily, 
          nrow = 4 , ncol = 2)
```

#### RD: DIN x Dust x Amm x Tot

```{r, fig.height= 7, fig.width=5}
ggarrange(din_rd, amm_rd, dust, tot_rd, 
          nrow = 4 , ncol = 1)
```

#### 

#### RD: Dust x Spp

```{r}
ggarrange(dust, rd_spp_daily,
          nrow = 2 , ncol = 1)
```

#### Total All Sites x Dust

```{r, fig.height=3.3, fig.width=3.5}
ggarrange(tot_bo, tot_c2, tot_rd, dust,
          nrow = 4 , ncol = 1)
```
